### 2019-02-03 draft.tex
relative,adaptative step and draft added.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{feynmp-auto}
\usepackage{tikz-feynman}
\usepackage{slashed}
\usepackage[vcentermath]{youngtab}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{enumerate}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{xcolor, colortbl}
\usepackage{longtable}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{xspace}
\usepackage{braket}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{float}
\usepackage{listings}
\usepackage{color}
\usepackage{tikz} 
\usetikzlibrary{shapes,arrows,positioning,automata,backgrounds,calc,er,patterns}
\usepackage{tikz-feynman}
\tikzfeynmanset{compat=1.0.0}

%
\usepackage[a4paper, left=1.5cm, right=1.5cm, top=2cm, bottom=2cm]{geometry}
\setlength{\parskip}{\baselineskip}
\date{\today}

\begin{document}

\title{
  Monte Carlo Bootstrap: current developments.
  }
\author{
  A. Laio, U. Luviano, M. Serone
}

%%Cuántica
\newcommand{\inty}{\int_{-\infty}^{\infty}} 
\newcommand{\Lag}{\mathcal{L}} 
\newcommand{\Id}{\mathbb{I}} 
\newcommand{\Tr}{\mathrm{Tr}} 
\newcommand{\tr}{\mathrm{tr}} 
\newcommand{\Det}{\mathrm{Det}} 
\newcommand{\gauge}{\mathcal{A}} 
\newcommand{\Lac}{\ensuremath{\mathbf{\hat{L}^2}}} 
\newcommand{\La}{\ensuremath{\mathbf{\hat{L}}}} 
\newcommand{\Ham}{\ensuremath{\hat{H}}} 
\renewcommand{\a}{\ensuremath{(e_1)}}
\renewcommand{\b}{\ensuremath{(e_2)}}
\renewcommand{\c}{\ensuremath{(e_3)}}
\newcommand\cd{\mathrel{\stackrel{\makebox[0pt]{\mbox{\normalfont\tiny
CD}}}{\longleftrightarrow}}}
\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
\newcommand{\then}{\ensuremath{\Rightarrow}}
\newcommand{\res}{\ensuremath{\mathrm{Res}}}
\newcommand{\R}{\ensuremath{\mathbb{R}}}
\newcommand{\integral}[1]{\ensuremath{\int_{a}^{b} #1 dt}}
%%%From Marco's
\def\UV{{\textsc{uv}}}
\def\IR{{\textsc{ir}}}
\def\gX{{g_\textsc{x}}}
\def\gY{{g_\textsc{y}}}
\def\dslash{\raisebox{1pt}{$\slash$} \hspace{-7pt} \partial}
\def\pslash{\raisebox{1pt}{$\slash$} \hspace{-7pt} p}
\def\qslash{\raisebox{1pt}{$\slash$} \hspace{-7pt} q}
\def\Aslash{\hspace{3pt}\raisebox{1pt}{$\slash$} \hspace{-9pt} A}
\def\Dslash{\hspace{3pt}\raisebox{1pt}{$\slash$} \hspace{-9pt} D}
\def\Dslashn{\hspace{3pt}\raisebox{1pt}{$\slash$} \hspace{-7pt} D}
\def\bea{\begin{eqnarray}} \def\eea{\end{eqnarray}}
\def\be{\begin{equation}} \def\ee{\end{equation}} \def\nn{\nonumber}
\def\a{& \hspace{-7pt}} \def\c{\hspace{-5pt}} \def\Z{{\bf Z}}
\def\zb{\overline{z}} \def\ov{\overline} \def\I{1\hspace{-4pt}1}
\def\ds{\displaystyle} \def\de{\partial} \def\deb{\ov{\partial}}
\def\dsl{\partial\hspace{-6pt}/} \def\psl{p\hspace{-5pt}/}
\def\taub{\bar \tau} \def\R{\mathcal R} \def\RR{   R}
\def\mc{\mathcal}
\def\ZZ{Z\hspace{-5pt}Z}
\def\CC{   C}
\def\b{\raisebox{14pt}{}\raisebox{-7pt}{}$\!\!$}
\def\tl{\tilde}
\def\Zeta{\ZZ}
\def\al{{\alpha^\prime}}
\def\hs{\hspace{10pt}}
\def\thp{\theta^\prime}
\def\thpt{\tilde\theta^\prime}
\def\w{\omega}
%\def\gg{{\bf g}}
\def\hh{{\bf h}}
\def\mut{\tilde \mu}
%
\newcommand{\Int}[2]{{\int}_{\hspace{-0.35cm}\begin{array}{c}\vspace{-0.35cm}
\\{\scriptstyle #1}\end{array}}\hspace{-0.35cm} #2}
\newcommand{\CInt}[2]{{\oint}_{\hspace{-0.35cm}\begin{array}{c}\vspace{-0.35cm}
\\{\scriptstyle #1}\end{array}}\hspace{-0.05cm} #2}
\newcommand{\diff}{\mathrm{d}}
\newcommand{\SO}{\text{SO}}
\newcommand{\SU}{\text{SU}}
\newcommand{\U}{\text{U}}
\newcommand{\G}{\mathcal{G}}

\newcommand{\egamma}[1]{\Gamma\!\left(#1\right)}
\newcommand{\rzeta}[1]{\zeta\!\left(#1\right)}
\setlength\arraycolsep{2pt}

\newcommand\tw[2]{
 \Bigg[\hspace{-1pt}\raisebox{1pt}
{$\begin{array}{c}
 \displaystyle{#1} \\ \displaystyle{#2}
 \end{array}$}
 \hspace{-1pt}\Bigg]}
\newcommand{\eqalign}[1]{\hspace{-10pt}\begin{array}{ll}#1\end{array}
\hspace{-10pt}}

\newcommand{\promille}{%
  \relax\ifmmode\promillezeichen
        \else\leavevmode\(\mathsurround=0pt\promillezeichen\)\fi}
\newcommand{\promillezeichen}{%
  \kern-.05em%
  \raise.5ex\hbox{\the\scriptfont0 0}%
  \kern-.15em/\kern-.15em%
  \lower.25ex\hbox{\the\scriptfont0 00}}

\newcommand{\Cr}{\star}

\newcommand{\ol}{\overline}
\newcommand{\wt}{\tilde}
\newcommand{\bs}{\boldsymbol}
\newcommand{\GR}{\mbox{\tiny $GR$ \normalsize}}
\newcommand{\abs}[1]{ \left| #1\right|}

%%%%%%%%%%%%%%%%%%%%
\maketitle

\section{Introduction}
The Conformal Bootstrap offers a way to chart the space of acceptable CFTs.

There has recently been a great revival of interest in the conformal bootstrap program \cite{Ferrara:1973yt,Polyakov:1974gs} after ref.\cite{Rattazzi:2008pe} observed that 
its applicability extends to Conformal Field Theories (CFTs) in $d>2$ dimensions. 
Since ref.\cite{Rattazzi:2008pe}, considerable progress has been achieved in understanding CFTs in $d\geq 2$ dimensions, both numerically and analytically.
Probably the most striking progress has been made in the numerical study of the 3D Ising model,
where amazingly precise operator dimensions and OPE coefficients have been determined
\cite{ElShowk:2012ht,El-Showk:2014dwa,Kos:2016ysd}.

\section{Bootstrap Basics.}
Consider the 4-point function of a scalar primary operator $\phi$ with scaling dimension $\Delta_\phi$: 
\be
\label{4-point-function}
\langle \phi(x_1) \phi(x_2) \phi(x_3) \phi(x_4) \rangle \, = \, \frac{g(z,\bar z)}{x_{12}^{2\Delta_\phi}x_{34}^{2\Delta_\phi} } \,,
\ee
where $z$ and $\bar z$ are so called conformally-invariant cross-ratios made up of $x_{ij}\equiv x_i-x_j$.
Applying the OPE to the operator pairs $\phi(x_1) \phi(x_2)$ and $\phi(x_3) \phi(x_4)$ in the 4-point function, one can write
\be
g(z,\bar z) = 1+\sum_{\Delta ,l } p_{\mathcal{O}} \, g_{\Delta,l}(z,\bar z) \,, 
\label{CBExp}
 \ee
where the sum runs over all primary operators $\mathcal{O}$ that appear in the $\phi\times \phi$ OPE with  $\Delta$ and $l$ being respectively their dimension and spin. Notice that $l$ has to be even
for identical scalars. For each primary, the sum over all its descendants is encoded in the conformal block function $g_{\Delta,l}(z,\bar z)$. Reflection positivity (i.e. unitarity) implies bounds on both the squared OPE coefficients $p_{\mathcal{O}}$
and the scaling dimensions $\Delta$:
\be
p_{\mathcal{O}} >0 \;\; \forall \mathcal{O}\,,  \quad
 \Delta \geq l+d-2 \;\; (l>0)\,, \quad \Delta \geq \frac{d-2}2 \;\; (l=0).
\ee
The sum over $\Delta$ (and hence over $l$) can be truncated up to a value $\Delta_*$. The following error estimate holds (for $\Delta_*\gg 1$):
\be
\Big|\sum_{(\Delta\geq \Delta_*),l}p_{\mathcal{O}} \, g_{\Delta,l}(z,\bar z)\Big| \, \leq \, \mathcal{R}(z,\bar z)\,,
\label{finalest4}
\ee
where
\be
\mathcal{R}(z,\bar z) \,\equiv \, \frac{(-\log|\rho(z)|)^{-4\Delta_\phi+1} \, 2^{4\Delta_\phi+1}}{\Gamma(4\Delta_\phi)} \frac{\Gamma(4\Delta_\phi, - \Delta_* \log |\rho(z)|)}{{(1-|\rho(z)|^2)}}\,.
\label{finalest5a}
\ee

Imposing crossing symmetry to the 4-point function (\ref{4-point-function}) gives, in any number of dimensions, 
\begin{align}
\label{bootstrapequation}
\sum_{\Delta ,l } p_{\mathcal{O}} \, \mathcal{F}_{\mathcal{O}}(z, \bar z) \, = \, (z \bar z)^{\Delta_\phi} - ((1-z)(1-\bar z))^{\Delta_\phi} \, ,
\end{align} 
where
\be
\mathcal{F}_{\mathcal{O}}(z, \bar z) \, \equiv \, ((1-z)(1-\bar z))^{\Delta_\phi} g_{\Delta,l}(z,\bar z)- (z \bar z)^{\Delta_\phi} g_{\Delta,l}(1-z,1-\bar z) \,.
\ee

\section{General Intuition of the MC bootstrap}
One can consider \ref{bootstrapequation} as a function of the spectrum and the
OPE coefficients, which should only be satisfied for physical conformal data.
Since any numerical approach involves truncating the OPE up to a maximum
dimension $\Delta^*$, it is important to estimate the remainder of the series in
order to bound the amount by which \ref{bootstrapequation} might be violated in
a given approximation. This was done by Rychkov et al 
%choro mareador sobre el error
%Escribir ecuación truncada

This motivates trying to find conformal data numerically using some sort of
gradient descent. In this case, one can take the truncated 
Bootstrap equations as a functional and minimize it with a Monte Carlo
simulation.

This naive approach proved to be untractable in the early stages of the
research, mostly because it became exponentially time consuming to look for more
operators. Thus, we decided to split the optimization in two steps. One that
finds an approximate spectrum without worrying for the OPE coefficients, and
then solving for the complete conformal data with a more refined Monte Carlo.
The first step was motivated by Gliozzi's determinant bootstrap, which we review
in the following section.

\section{Review of Gliozzi's paper}
yadda yadda matrix, solution

\section{LogDet implementation}
Given a putative spectrum, the determinant of the matrix
\subsection{naive approach}
\subsection{Cross smearing}
\subsection{Recursive with check}

\section{$\chi^2$ refinement}
\subsection{cWLS as a way to determine OPEs}

\section{Summary of results}
\subsection{Free CFT in 4d}
\subsection{GFT in 1d}
\subsection{GFT in 4d}

  \end{document}

### 2019-02-03 towards_a_grand_unified_script.m

@@ -13,33 +13,9 @@ $MinPrecision=MachinePrecision;
       \[Rho]intErrorEstimateFt[d_, DDs_, z_, \[Gamma]_] := 
      v^d*\[Rho]intErrorEstimateG[d, DDs, z, \[Gamma]] + u^d*\[Rho]intErrorEstimateG[d, DDs, 1 - z, \[Gamma]] /. {u -> z*Conjugate[z], v -> (1 - z)*(1 - Conjugate[z])}; 
      (*coefficients and prefactors*)
-    kfunctAna[\[Beta]_, x_] := Exp[(\[Beta]/2)*Log[4*((1 - Sqrt[1 - x])^2/x)]]*(x/(2*(1 - x)^(1/4)*(1 - Sqrt[1 - x]))); 
-    ConformalBlockAna[DD_, l_, z_] := ((-1)^l/2^l)*((z*Conjugate[z])/(z - Conjugate[z]))*(kfunctAna[DD + l, z]*kfunctAna[DD - l - 2, Conjugate[z]] - 
-       kfunctAna[DD + l, Conjugate[z]]*kfunctAna[DD - l - 2, z]);
-       (*derivatives*)
-       FAnaDer[DD_, l_, z_] := (1/(z - Conjugate[z]))*(-1)^(2*l)*(1 - z)*z*
-      (1 - Conjugate[z])*Conjugate[z]*(-((2^(-5 + 2*DD)*((1 - Sqrt[z])/(1 + Sqrt[z]))^((1/2)*(-2*l + DD))*(1 - z)*
-          ((1 - Sqrt[Conjugate[z]])/(1 + Sqrt[Conjugate[z]]))^((1/2)*(-2*l + DD))*(-((1 - Sqrt[z])/(1 + Sqrt[z]))^(2*l) - 
-           Sqrt[z]*(((1 - Sqrt[z])/(1 + Sqrt[z]))^(2*l) + ((1 - Sqrt[Conjugate[z]])/(1 + Sqrt[Conjugate[z]]))^(2*l)) + 
-           ((1 - Sqrt[Conjugate[z]])/(1 + Sqrt[Conjugate[z]]))^(2*l) + (((1 - Sqrt[z])/(1 + Sqrt[z]))^(2*l) + 
-             Sqrt[z]*(((1 - Sqrt[z])/(1 + Sqrt[z]))^(2*l) - ((1 - Sqrt[Conjugate[z]])/(1 + Sqrt[Conjugate[z]]))^(2*l)) + 
[…]

### 2019-02-03 draft.tex
minor changes to draft

@@
 Consider the 4-point function of a scalar primary operator $\phi$ with scaling dimension $\Delta_\phi$: 
-\be
+\begin{equation}
 \label{4-point-function}
 \langle \phi(x_1) \phi(x_2) \phi(x_3) \phi(x_4) \rangle \, = \, \frac{g(z,\bar z)}{x_{12}^{2\Delta_\phi}x_{34}^{2\Delta_\phi} } \,,
-\ee
+\end{equation}
 where $z$ and $\bar z$ are so called conformally-invariant cross-ratios made up of $x_{ij}\equiv x_i-x_j$.
 Applying the OPE to the operator pairs $\phi(x_1) \phi(x_2)$ and $\phi(x_3) \phi(x_4)$ in the 4-point function, one can write
-\be
+\begin{equation}
 g(z,\bar z) = 1+\sum_{\Delta ,l } p_{\mathcal{O}} \, g_{\Delta,l}(z,\bar z) \,, 
 \label{CBExp}
- \ee
+ \end{equation}
 where the sum runs over all primary operators $\mathcal{O}$ that appear in the $\phi\times \phi$ OPE with  $\Delta$ and $l$ being respectively their dimension and spin. Notice that $l$ has to be even
@@
 and the scaling dimensions $\Delta$:
-\be
+\begin{equation}
 p_{\mathcal{O}} >0 \;\; \forall \mathcal{O}\,,  \quad
  \Delta \geq l+d-2 \;\; (l>0)\,, \quad \Delta \geq \frac{d-2}2 \;\; (l=0).
-\ee
-The sum over $\Delta$ (and hence over $l$) can be truncated up to a value $\Delta_*$. The following error estimate holds (for $\Delta_*\gg 1$):
-\be
-\Big|\sum_{(\Delta\geq \Delta_*),l}p_{\mathcal{O}} \, g_{\Delta,l}(z,\bar z)\Big| \, \leq \, \mathcal{R}(z,\bar z)\,,
-\label{finalest4}
-\ee
-where
-\be
-\mathcal{R}(z,\bar z) \,\equiv \, \frac{(-\log|\rho(z)|)^{-4\Delta_\phi+1} \, 2^{4\Delta_\phi+1}}{\Gamma(4\Delta_\phi)} \frac{\Gamma(4\Delta_\phi, - \Delta_* \log |\rho(z)|)}{{(1-|\rho(z)|^2)}}\,.
-\label{finalest5a}
-\ee
+\end{equation}
 
@@
 where
-\be
+\begin{equation}
 \mathcal{F}_{\mathcal{O}}(z, \bar z) \, \equiv \, ((1-z)(1-\bar z))^{\Delta_\phi} g_{\Delta,l}(z,\bar z)- (z \bar z)^{\Delta_\phi} g_{\Delta,l}(1-z,1-\bar z) \,.
-\ee
+\end{equation}
 
@@
 order to bound the amount by which \ref{bootstrapequation} might be violated in
-a given approximation. This was done by Rychkov et al 
-%choro mareador sobre el error
-%Escribir ecuación truncada
+a given approximation. This was done by Rychkov et al,
+who found the following error estimate holds (for $\Delta_*\gg 1$):
+\begin{equation}
+\Big|\sum_{(\Delta\geq \Delta_*),l}p_{\mathcal{O}} \, g_{\Delta,l}(z,\bar z)\Big| \, \leq \, \mathcal{R}(z,\bar z)\,,
+\label{finalest4}
+\end{equation}
+where
+\begin{equation}
+\mathcal{R}(z,\bar z) \,\equiv \, \frac{(-\log|\rho(z)|)^{-4\Delta_\phi+1} \, 2^{4\Delta_\phi+1}}{\Gamma(4\Delta_\phi)} \frac{\Gamma(4\Delta_\phi, - \Delta_* \log |\rho(z)|)}{{(1-|\rho(z)|^2)}}\,.
+\label{finalest5a}
+\end{equation}
 
@@
 Bootstrap equations as a functional and minimize it with a Monte Carlo
-simulation.
+simulation. Concretely, one can rewrite the bootstrap equations as
 

### 2019-02-03 towards_a_grand_unified_script.m
just in case

@@ -156,7 +156,7 @@ $MinPrecision=prec;
           \[CapitalDelta]LOld=\[CapitalDelta]L;
           QQold=QQ0;  
 
-  dimToVary = RandomInteger[{1,lmax}];
+  dimToVary =If[it==1,RandomInteger[{1,lmax}], RandomInteger[{1,lmax-nzeros}]];
        (*Shift one dimension by a random amount*)       
           \[CapitalDelta]L[[dimToVary,1]] = \[CapitalDelta]L[[dimToVary,1]]+ RandomVariate[NormalDistribution[0, sigmamods[[dimToVary]] sigmaMC]];
 (*Reevaluate coefficients*)
@@ -174,12 +174,13 @@ errSample=Table[ \[Rho]intErrorEstimateFt[\[CapitalDelta]\[Phi],\[CapitalDelta]L
 res=(results[[1]].QQ0-Idsample)/errSample;
 nzerosnew=Count[results[[1]],0];
 fracvionew=Count[Abs[res]<1//Thread,False]/Nz;
-Print[{nzerosnew,fracvionew}];
+(*Print[{nzerosnew,fracvionew}];
+*)
 
           If[fracvionew<fracvio || nzeros>nzerosnew, fracvio = fracvionew;nzeros=nzerosnew;sigmamods[[dimToVary]] =sigmamods[[dimToVary]] (101/100),\[CapitalDelta]L=\[CapitalDelta]LOld;QQ0=QQold;sigmamods[[dimToVary]] =sigmamods[[dimToVary]] (99/100)];
 $MinPrecision=10;
    dw=\[CapitalDelta]L[[All,1]];
-          Sow[ {it, dw,results[[1]], {nzerosnew,fracvionew}}],
+          Sow[ {it, dw,results[[1]], {nzeros,fracvio}}],
      {it, 1, Ndit}]]; 
 $MinPrecision=3;
[…]

### 2019-02-03 towards_a_grand_unified_script.m
corrected naming issue

@@ -109,7 +109,7 @@ $MinPrecision=3;
 (*MC routine-Chi2*)
 MetroGoFixedSelectiveDirChi2[\[CapitalDelta]\[Phi]_,\[CapitalDelta]LOriginal_,Nz_,Ndit_,prec_,betad_,seed_,sigmaMC_,dcross_,lmax_,idTag_,sigmaz_]:=Block[{itd, DDldata, sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
     zsample, Idsample,  PP0, PP1, lr, nr, Errvect, Factor, Factor0, ppm, DDldataEx, PPEx, QQEx, Idsampleold, ip, nvmax, QQFold,  
-    IdsampleEx,zOPE,QQOPE,Calc,coeffTemp,Ident,OPEcoeff,ActionTot,  TotD ,DDldataold,QQold,\[CapitalDelta]LOld,dimToVary,PP,QQsave,\[CapitalDelta]L,dw,errSample,results,nzeros=Length[\[CapitalDelta]LOriginal],fracvio=100,nzerosnew,fracvionew,res,sigmamods=ConstantArray[1,Length[\[CapitalDelta]LOriginal]]}, 
+    IdsampleEx,zOPE,QQOPE,Calc,coeffTemp,Ident,OPEcoeff,ActionTot,  TotD ,DDldataold,QQold,resultsOld,\[CapitalDelta]LOld,dimToVary,PP,QQsave,\[CapitalDelta]L,dw,errSample,results,nzeros=Length[\[CapitalDelta]LOriginal],fracvio=100,nzerosnew,fracvionew,res,sigmamods=ConstantArray[1,Length[\[CapitalDelta]LOriginal]]}, 
     (*precision*)
 SetOptions[{RandomReal,RandomVariate},WorkingPrecision->prec];
 $MaxPrecision=prec;
@@ -130,7 +130,8 @@ Idsample = SetPrecision[Table[(zsample[[zv]]*Conjugate[zsample[[zv]]])^\[Capital
 TotD =   Reap[ Do[
 $MinPrecision=prec;
           \[CapitalDelta]LOld=\[CapitalDelta]L;
-          QQold=QQ0;  
+          QQold=QQ0; 
+          resultsOld=results; 
 
[…]

### 2019-02-04 draft.tex
mc final calculation crashing unexpectedly.

@@
 \usepackage{tikz-feynman}
+
+\numberwithin{equation}{section}
 \tikzfeynmanset{compat=1.0.0}
@@
  \Delta \geq l+d-2 \;\; (l>0)\,, \quad \Delta \geq \frac{d-2}2 \;\; (l=0).
+  \label{unit-bound}
 \end{equation}
@@
 gradient descent. In this case, one can take the truncated 
-Bootstrap equations as a functional and minimize it with a Monte Carlo
+Bootstrap equations as a function of a discrete spectrum and OPE coefficients 
+and minimize it with a Monte Carlo
 simulation. Concretely, one can rewrite the bootstrap equations as
 
+\begin{equation}
+\label{bootstrapequation-bound}
+\sum_{\Delta<\Delta^* ,l } p_{\mathcal{\Delta},l} \,
+  \mathcal{F}_{\mathcal{O}}(z, \bar z) \, = \, (z \bar z)^{\Delta_\phi} -
+  ((1-z)(1-\bar z))^{\Delta_\phi} + \mathcal{E}(z,\bar z),
+\end{equation}
+
+where $l$ is bounded in turn by
+  \ref{unit-bound}, and 
+\begin{equation}
+\label{error-bound}
+  \mathcal{E}(z,\bar z) \leq \mathcal{E}_{\mathrm{max}}(z,\bar z) \equiv
+  v^{\Delta_\phi}\mathcal{R}(z,\bar z)
+  +
+  u^{\Delta_\phi}\mathcal{R}(1-z,1-\bar z).
+\end{equation}
+
+Since these equations have to be satisfied everywhere outside the branch cut at
+\([1,\infty)\), one can take a finite set of points $\{z_i\}_{i=1}^{N_z}$ and
+write \ref{bootstrapequation-bound} as
+\begin{equation}
+  \mathcal{M}\cdot \vec{\rho} = \vec{\sigma} + \vec{\epsilon}
+\label{matrix-boo}
+\end{equation}
+
+where 
+\begin{equation}
+\vec{\sigma} \, \equiv \, \left( \begin{matrix}
+                      |z_1|^{2\Delta_\phi} \, - \, |1-z_1|^{2 \Delta_\phi}\\  |z_2|^{2\Delta_\phi} \, - \, |1-z_2|^{2 \Delta_\phi} \\ \vdots
+                     \end{matrix} \right) 
+                     \quad \, \text{and} \, \quad 
+                      \vec{\epsilon} \, \equiv \, 
+                          \left( \begin{matrix}
+                                  \mathcal{E}(z_1,\bar z_1,\Delta_*,\Delta_\phi) \\
+                                  \mathcal{E}(z_2,\bar z_2,\Delta_*,\Delta_\phi) \\
+                                  \vdots
+                                 \end{matrix} \right)  \, .
+\end{equation}
+
+and
+\begin{equation}
+\mathcal{M} \, \equiv \, \left( \begin{matrix}
+  \mathcal{F}_{\Delta_1,l_1}(z_1, \bar z_1) &\mathcal{F}_{\Delta_2,l_2}(z_1, \bar
+  z_1) & \cdots \\
+  \mathcal{F}_{\Delta_1,l_1}(z_2, \bar z_2) &\mathcal{F}_{\Delta_2,l_2}(z_2, \bar
+  z_2) & \cdots \\
+  \vdots  & \vdots &\ddots\\
+                     \end{matrix} \right) .
+                     \label{matrix-op}
+\end{equation}
+
+The straightforward path is to define a cost function
+\[
+  C\sim | \mathcal{M}\cdot \vec{\rho} - \vec{\sigma} |
+\]
+and minimize it stochastically.
 This naive approach proved to be untractable in the early stages of the
@@
 operators. Thus, we decided to split the optimization in two steps. One that
-finds an approximate spectrum without worrying for the OPE coefficients, and
+finds an approximate spectrum without worrying about the OPE coefficients, and
 then solving for the complete conformal data with a more refined Monte Carlo.
@@
 \section{LogDet implementation}
-Given a putative spectrum, the determinant of the matrix
+Given a putative spectrum, the determinant of \ref{matrix-op}
+should get closer to zero as we approach a physically sensible set of operator
+dimensions. Since the determinant
 \subsection{naive approach}

### 2019-02-04 towards_a_grand_unified_script.m

@@ -132,7 +132,7 @@ $MinPrecision=prec;
           \[CapitalDelta]LOld=\[CapitalDelta]L;
           QQold=QQ0; 
           resultsOld=results; 
-
+(*This If avoids varying operators which still don't enter the OPE*)
   If[it==1,dimToVary = RandomInteger[{1,lmax}],dimToVary = RandomInteger[{1,lmax-nzeros}]];
        (*Shift one dimension by a random amount*)       
           \[CapitalDelta]L[[dimToVary,1]] = \[CapitalDelta]L[[dimToVary,1]]+ RandomVariate[NormalDistribution[0, sigmamods[[dimToVary]] \[CapitalDelta]L[[dimToVary,1]] sigmaMC]];
@@ -561,25 +561,16 @@ ParallelTable[mcIterator[1,4,9,\[CapitalDelta]L,\[Beta]list,500,88,1000+50tol,ni
 ParallelTable[metroReturnAvgChi2[100,3000,200,10^(-i),deltamc[[2]],10+i,4,"delta2",1/10,10^(-i)],{i,3,4}]
 
 
-ParallelTable[metroReturnAvgChi2[100,3000,200,10^(-i),deltamc[[3]],10+i,4,"delta3",1/10,10^(-i)],{i,3,4}]
+Table[metroReturnAvgChi2[100,1500,200,10^(-i),deltamc[[3]],10+i,4,"delta3",1/10,10^(-i)],{i,3,4}]
 
 
-ParallelTable[metroReturnAvgChi2[100,3000,1000,10^(-i),deltamc[[2]],10+i,4,"delta2",1/10,10^(-i)],{i,3,4}]
+Table[metroReturnAvgChi2[100,1500,1000,10^(-i),deltamc[[2]],10+i,4,"delta2",1/10,10^(-i)],{i,3,4}]
 
 
-ParallelTable[metroReturnAvgChi2[100,3000,1000,10^(-i),deltamc[[3]],10+i,4,"delta3",1/10,10^(-i)],{i,3,4}]
+Table[metroReturnAvgChi2[100,1500,1000,10^(-i),deltamc[[3]],10+i,4,"delta3",1/10,10^(-i)],{i,3,4}]
 
 
-metroReturnAvgChi2[88,5000,500,1/100,deltamc[[2]],3421,4,"adaptative-test",1/10,1/100]
-
-
[…]

### 2019-02-04 draft.tex
fun with draft

@@
 \label{error-bound}
-  \mathcal{E}(z,\bar z) \leq \mathcal{E}_{\mathrm{max}}(z,\bar z) \equiv
+  |\mathcal{E}(z,\bar z)| \leq \mathcal{E}_{\mathrm{max}}(z,\bar z) \equiv
   v^{\Delta_\phi}\mathcal{R}(z,\bar z)
@@
 \section{Review of Gliozzi's paper}
-yadda yadda matrix, solution
+In 2013, Gliozzi realized that, for $N_z$ bigger than the number of operators
+one considered in the OPE, \ref{matrix-boo} represented an over-determined
+Linear System. Thus, in order for a solution (that is, a set of OPE coefficients
+satisfying crossing) to exist, each minor should vanish.
 
 \section{LogDet implementation}
+\subsection{naive approach}
 Given a putative spectrum, the determinant of \ref{matrix-op}
 should get closer to zero as we approach a physically sensible set of operator
-dimensions. Since the determinant
-\subsection{naive approach}
+dimensions. Since this quantity could range over many orders of magnitude, we
+decided to square it and then take the $\log$ of it. This proved to be
+numerically troubling, since the behaviour of the logarithm around $0$ is far
+from differentiable and the landscape was thus full of spurious minima out of
+which the Metropolis algorithm could not get out.
 \subsection{Cross smearing}
+In order to smooth this behaviour out, we implemented an empirical
+renormalization that consists in computing the value of the determinant at
+adjacent points to the main one. Thus
+\[
+\begin{aligned}
+  S({\Delta_i,l_i})& = \log\Det^2\mathcal{M}(\{\Delta_i,l_i\})\\
+  \to
+  S_{\mathrm{cross}}(\{\Delta_i,l_i\})  & =   \log\Det^2\mathcal{M}(\{\Delta_i,l_i\}) + \sum_i\left(
+  \log\Det^2\mathcal{M}(\{\Delta_i+\delta,l_i\})  +
+  \log\Det^2\mathcal{M}(\{\Delta_i-\delta,l_i\})  \right)
+\end{aligned}
+\]
+
+This action was much more efficient at finding the correct dimensions for the
+free theory, and numerical exploration showed that the basin of attraction for
+each given operator's dimension was very sharp, as long as the other ones were
+kept at the exact value. Small perturbations destroyed this basin rather
+quickly, and thus it was hard to get the MC routine to solve for a large number
+of operators  ($\sim 7$)at the same time.
+
 \subsection{Recursive with check}
+The next breakthrough in the routine came when we decided to start with few
+($\sim 4$) operators and add the next operators one by one. To avoid spoiling
+the previous solution, only the new operator was varied for a given number of
+steps before we allowed the whole spectrum to be optimized. This gave a very
+efficient routine with a large radius of convergence.
+
+This recursive step was further improved by using
+\ref{error-bound} to bound \ref{matrix-boo} as 
+\begin{equation}
+  | \mathcal{M}\cdot \vec{\rho}-\vec{\sigma} | < \vec{\epsilon_{\mathrm{max}}}.
+  \label{cross-check}
+\end{equation}
+Then, the result of each end state of the MC could be tested to see if it
+satisfied Crossing Symmetry with the precision correspoinding to the $\Delta^*$
+considered. Otherwise, it changed the seed of the pseudorandom generator and
+started again the MC.
 
@@
 
+\begin{thebibliography}{10}
+
+ \bibitem{Ferrara:1973yt}
+  S.~Ferrara, A.~F.~Grillo and R.~Gatto,
+  ``Tensor representations of conformal algebra and conformally covariant operator product expansion,''
+  Annals Phys.\  {\bf 76} (1973) 161.
+  %%CITATION = APNYA,76,161;%%
+  %88 citations counted in INSPIRE as of 18 Nov 2014
+  %  \bibitem{Ferrara:1973eg}
+
+  \bibitem{Polyakov:1974gs}
+  A.~M.~Polyakov,
+  ``Nonhamiltonian approach to conformal quantum field theory,''
+  Zh.\ Eksp.\ Teor.\ Fiz.\  {\bf 66} (1974) 23.
+  %%CITATION = ZETFA,66,23;%%
+  %67 citations counted in INSPIRE as of 10 Jun 2014
+
+\bibitem{Rattazzi:2008pe}
+  R.~Rattazzi, V.~S.~Rychkov, E.~Tonni and A.~Vichi,
+  ``Bounding scalar operator dimensions in 4D CFT,''
+  JHEP {\bf 0812} (2008) 031
+  [arXiv:0807.0004 [hep-th]].
+  %%CITATION = ARXIV:0807.0004;%%
+  %171 citations counted in INSPIRE as of 13 May 2015
+
+ \bibitem{ElShowk:2012ht}
+  S.~El-Showk, M.~F.~Paulos, D.~Poland, S.~Rychkov, D.~Simmons-Duffin and A.~Vichi,
+  ``Solving the 3D Ising Model with the Conformal Bootstrap,''
+  Phys.\ Rev.\ D {\bf 86} (2012) 025022
+  doi:10.1103/PhysRevD.86.025022
+  [arXiv:1203.6064 [hep-th]].
+  %%CITATION = doi:10.1103/PhysRevD.86.025022;%%
+  %156 citations counted in INSPIRE as of 13 Apr 2016
+
+    \bibitem{El-Showk:2014dwa}
+  S.~El-Showk, M.~F.~Paulos, D.~Poland, S.~Rychkov, D.~Simmons-Duffin and A.~Vichi,
+  ``Solving the 3d Ising Model with the Conformal Bootstrap II. c-Minimization and Precise Critical Exponents,''
+  J.\ Stat.\ Phys.\  {\bf 157} (2014) 869
+  doi:10.1007/s10955-014-1042-7
+  [arXiv:1403.4545 [hep-th]].
+  %%CITATION = doi:10.1007/s10955-014-1042-7;%%
+  %95 citations counted in INSPIRE as of 13 Apr 2016
+
+   \bibitem{Kos:2016ysd}
+  F.~Kos, D.~Poland, D.~Simmons-Duffin and A.~Vichi,
+  ``Precision Islands in the Ising and $O(n)$ Models,''
+  arXiv:1603.04436 [hep-th].
+  %%CITATION = ARXIV:1603.04436;%%
+  %3 citations counted in INSPIRE as of 13 Apr 2016
+
+  \bibitem{Kos:2013tga}
+  F.~Kos, D.~Poland and D.~Simmons-Duffin,
+  ``Bootstrapping the $O(n)$ vector models,''
+  JHEP {\bf 1406} (2014) 091
+  doi:10.1007/JHEP06(2014)091
+  [arXiv:1307.6856 [hep-th]].
+  %%CITATION = doi:10.1007/JHEP06(2014)091;%%
+  %85 citations counted in INSPIRE as of 13 Apr 2016
+
+\end{thebibliography}
+
   \end{document}

### 2019-02-04 draft.tex
fun with draft

@@
 \subsection{Recursive with check}
+\label{rec-check}
+
 The next breakthrough in the routine came when we decided to start with few
@@
 \begin{equation}
-  | \mathcal{M}\cdot \vec{\rho}-\vec{\sigma} | < \vec{\epsilon_{\mathrm{max}}}.
+  | \mathcal{M}\cdot \vec{\rho}-\vec{\sigma} | < \vec{\epsilon}_{\mathrm{max}}.
   \label{cross-check}
@@
 \subsection{cWLS as a way to determine OPEs}
+Since the dependence of \ref{cross-check} on $\vec{\rho}$ is linear, for
+$N_z>N_{Op}$ it is possible to find the set of OPE coefficients that best
+satisfy crossing via the Weighted Least Squares method\footnote{Should we add a
+reference here, other than Wikipedia?}. For a generic spectrum
+obtained via the method described in section \ref{rec-check}, this naive set of OPE
+coefficients will have some negative components, which stems from the
+fact that our spectrum is only approximate. Since the error estimate depends
+crucially on the positivity of the OPE coefficients, we need to find the
+solution that minimizes \ref{cross-check} and has all entries non-negative. This
+is attained by setting the first negative OPE coefficient (from back to forth,
+if $\Delta_i<\Delta_{i+1}$) and then running a WLS routine with the remaining
+entries. If this solution still has negative entries, the proccedure is repeated
+until an acceptable $\vec{\rho}$ is obtained.
+
+It is an interesting fact observed in the cases studied so far, that this
+constrained solution doesn't satisfy crossing with the error estimate
+corresponding to the original $\Delta^*$, but once we consider the zeros in
+$\vec{\rho}$, which effectively remove higher dimensional operators from the
+OPE, \ref{cross-check} is satisfied.
+
+For properly chosen
+points in $z$, not all the inequalties in \ref{cross-check} will be satisfied,
+one can then take this number and try to minimize it with another Monte Carlo
+routine.
 

### 2019-02-05 towards_a_grand_unified_script.m
problem is in stdv

@@ -186,13 +186,15 @@ MetroGoFixedSelectiveDir[\[CapitalDelta]\[Phi],\[CapitalDelta]L,nit,prec,\[Beta]
 data= Get["Res-fixed_Param_Nit="<>ToString[nit]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[\[Beta],3]]<>"sigmaMC="<>ToString[N[1/10,3]]<>"dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]<>"id="<>ToString[Length[\[CapitalDelta]L]]<>idtag<>".txt"];
 Export["Plot-fixed_Param_Nit="<>ToString[nit]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[\[Beta],3]]<>"sigmaMC="<>ToString[N[1/10,3]]<>"dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]<>"id="<>ToString[Length[\[CapitalDelta]L]]<>".pdf",ListPlot[Table[data[[All,2]][[All,i]],{i,1,Length[\[CapitalDelta]L]}],Joined->True,GridLines->Automatic,PlotStyle->Thin,PlotLabel->ToString[Length[\[CapitalDelta]L]]<>"Nit="<>ToString[nit]<>" prec="<>ToString[prec]<>" beta="<>ToString[N[\[Beta],3]]<>" sigmaMC="<>ToString[N[1/10,3]]<>" dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]]];
[…]

### 2019-02-05 towards_a_grand_unified_script.m
avg routine now working -- no std

@@ -193,7 +193,7 @@ MetroGoFixedSelectiveDirChi2[1,\[CapitalDelta]L,Nz,nit,prec,\[Beta],seed,sigmaMC
 data= Get["Res-chi_Param_Nit="<>ToString[nit]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[\[Beta],3]]<>"sigmaMC="<>ToString[N[sigmaMC,3]]<>"dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]<>"Nz="<>ToString[Nz]<>"id="<>idtag<>".txt"];
 Export["zoom-Plot-chi_Param_Nit="<>ToString[nit]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[\[Beta],3]]<>"sigmaMC="<>ToString[N[sigmaMC,3]]<>"dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]<>"Nz="<>ToString[Nz]<>"id="<>idtag<>".pdf",ListPlot[Table[data[[All,2]][[All,i]]-2i+1,{i,1,Length[\[CapitalDelta]L]}],Joined->True,GridLines->Automatic,PlotStyle->Thin,PlotRange->{{0,nit},{9/10,11/10}},PlotLegends->\[CapitalDelta]L[[;;,2]],PlotLabel->ToString[Length[\[CapitalDelta]L]]<>"Nit="<>ToString[nit]<>" prec="<>ToString[prec]<>" beta="<>ToString[N[\[Beta],3]]<>" sigmaMC="<>ToString[N[1/10,3]]<>" dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]]];
 (*{Mean[data[[nit-100;;nit,2]]],StandardDeviation[data[[nit-100;;nit,2]]],Mean[data[[nit-100;;nit,3]]],StandardDeviation[data[[nit-100;;nit,3]]]}*)
-Return[{data[[nit-100;;nit,3]]}];
+Return[{data[[nit-100;;nit,2]]//Mean,data[[nit-100;;nit,3]]//Mean}];
 ];
 
[…]

### 2019-02-05 draft.tex
started adding chi restarter. Need to tune tolerance.

@@
 OPE coefficients, which should only be satisfied for physical conformal data.
-Since any numerical approach involves truncating the OPE up to a maximum
+Since almost any numerical approach involves truncating the OPE up to a maximum
 dimension $\Delta^*$, it is important to estimate the remainder of the series in
@@
 \]
-and minimize it stochastically.
+and minimize it stochastically\footnote{Should I add a section on Metropolis MC
+here?}.
 This naive approach proved to be untractable in the early stages of the
@@
 decided to square it and then take the $\log$ of it. This proved to be
-numerically troubling, since the behaviour of the logarithm around $0$ is far
-from differentiable and the landscape was thus full of spurious minima out of
+numerically troubling due to the behaviour of the logarithm around $0$  and the landscape was thus full of spurious minima out of
 which the Metropolis algorithm could not get out.
+
 \subsection{Cross smearing}
@@
   S_{\mathrm{cross}}(\{\Delta_i,l_i\})  & =   \log\Det^2\mathcal{M}(\{\Delta_i,l_i\}) + \sum_i\left(
-  \log\Det^2\mathcal{M}(\{\Delta_i+\delta,l_i\})  +
-  \log\Det^2\mathcal{M}(\{\Delta_i-\delta,l_i\})  \right)
+  \log\Det^2\mathcal{M}(\cdots,\{\Delta_i+\delta,l_i\},\cdots)  +
+  \log\Det^2\mathcal{M}(\cdots,\{\Delta_i-\delta,l_i\},\cdots)  \right)
 \end{aligned}
@@
 quickly, and thus it was hard to get the MC routine to solve for a large number
-of operators  ($\sim 7$)at the same time.
+of operators  ($\sim 7$) at the same time.
 
@@
 The next breakthrough in the routine came when we decided to start with few
-($\sim 4$) operators and add the next operators one by one. To avoid spoiling
+($\sim 4$) operators, find the operator dimensions which minimized the 
+action and then add the next operators one by one. To avoid spoiling
 the previous solution, only the new operator was varied for a given number of
@@
 \section{$\chi^2$ refinement}
-\subsection{cWLS as a way to determine OPEs}
+\subsection{cWLS as a way to determine the OPE coefficients}
 Since the dependence of \ref{cross-check} on $\vec{\rho}$ is linear, for
@@
 satisfy crossing via the Weighted Least Squares method\footnote{Should we add a
-reference here, other than Wikipedia?}. For a generic spectrum
+reference here, other than Wikipedia?}. 
+For a generic spectrum
 obtained via the method described in section \ref{rec-check}, this naive set of OPE
 coefficients will have some negative components, which stems from the
-fact that our spectrum is only approximate. Since the error estimate depends
+fact that our spectrum is only approximate. Since the error estimate
+\ref{finalestimate5a}
+depends
 crucially on the positivity of the OPE coefficients, we need to find the

### 2019-02-05 towards_a_grand_unified_script.m

@@ -107,8 +107,8 @@ $MinPrecision=3;
       Export["Res-fixed_Param_Nit="<>ToString[Ndit]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[betad,3]]<>"sigmaMC="<>ToString[N[sigmaMC,3]]<>"dcross="<>ToString[N[dcross,3]]<>"seed="<>ToString[seed]<>"id="<>idTag<>".txt", TotD[[2]]];]
 
 (*MC routine-Chi2*)
-MetroGoFixedSelectiveDirChi2[\[CapitalDelta]\[Phi]_,\[CapitalDelta]LOriginal_,Nz_,Ndit_,prec_,betad_,seed_,sigmaMC_,dcross_,lmax_,idTag_,sigmaz_]:=Block[{itd, DDldata, sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
-    zsample, Idsample,  PP0, PP1, lr, nr, Errvect, Factor, Factor0, ppm, DDldataEx, PPEx, QQEx, Idsampleold, ip, nvmax, QQFold,  
+MetroGoFixedSelectiveDirChi2[\[CapitalDelta]\[Phi]_,\[CapitalDelta]LOriginal_,Nz_,Ndit_,prec_,betad_,seed0_,sigmaMC_,dcross_,lmax_,idTag_,sigmaz_]:=Block[{itd, DDldata, sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
+    zsample, Idsample,  PP0, PP1, lr, nr, Errvect, Factor, Factor0, seed=seed0, ppm, DDldataEx, PPEx, QQEx, Idsampleold, ip, nvmax, QQFold,  
     IdsampleEx,zOPE,QQOPE,Calc,coeffTemp,Ident,OPEcoeff,ActionTot,  TotD ,DDldataold,QQold,resultsOld,\[CapitalDelta]LOld,dimToVary,PP,QQsave,\[CapitalDelta]L,dw,errSample,results,nzeros=Length[\[CapitalDelta]LOriginal],fracvio=100,nzerosnew,fracvionew,res,sigmamods=ConstantArray[1,Length[\[CapitalDelta]LOriginal]]}, 
[…]

### 2019-02-05 draft.tex
added tol to chi-restarter. minor changes to draft.

@@
 order to bound the amount by which \ref{bootstrapequation} might be violated in
-a given approximation. This was done by Rychkov et al,
+a given approximation. This was done by \cite{Pappadopulo:2012jk},
 who found the following error estimate holds (for $\Delta_*\gg 1$):
@@
 \[
-  C\sim | \mathcal{M}\cdot \vec{\rho} - \vec{\sigma} |
+  C(\Delta_i,\vec\rho)\sim | \mathcal{M}(\Delta_i)\cdot \vec{\rho} - \vec{\sigma} |
 \]
-and minimize it stochastically\footnote{Should I add a section on Metropolis MC
+and minimize it stochastically over the space of $\{\Delta_i,\vec\rho\}$ \footnote{Should I add a section on Metropolis MC
 here?}.
@@
 research, mostly because it became exponentially time consuming to look for more
-operators. Thus, we decided to split the optimization in two steps. One that
-finds an approximate spectrum without worrying about the OPE coefficients, and
-then solving for the complete conformal data with a more refined Monte Carlo.
+operators. Thus, we decided to split the optimization into two steps. First, we
+find an approximate spectrum without worrying about the OPE coefficients, and
+then solve for the complete conformal data with a more refined Monte Carlo.
 The first step was motivated by Gliozzi's determinant bootstrap, which we review
@@
 \section{Review of Gliozzi's paper}
-In 2013, Gliozzi realized that, for $N_z$ bigger than the number of operators
-one considered in the OPE, \ref{matrix-boo} represented an over-determined
+In 2013, \cite{Gliozzi:2013ysa} realized that, for $N_z$ bigger than the number of operators
+one considered in the OPE ($N_{Op}$), \ref{matrix-boo} represented an over-determined
 Linear System. Thus, in order for a solution (that is, a set of OPE coefficients
@@
 \begin{aligned}
-  S({\Delta_i,l_i})& = \log\Det^2\mathcal{M}(\{\Delta_i,l_i\})\\
+  S(\{\Delta_i,l_i\})& = \log\Det^2\mathcal{M}(\{\Delta_i,l_i\})\\
   \to
@@
 \begin{equation}
-  | \mathcal{M}\cdot \vec{\rho}-\vec{\sigma} | < \vec{\epsilon}_{\mathrm{max}}.
+  | \mathcal{M}\cdot \vec{\rho}-\vec{\sigma} | < \vec{\epsilon}_{\mathrm{max}},
   \label{cross-check}
 \end{equation}
+where $\vec \epsilon _{\mathrm{max}}$ is just $\vec \epsilon$ under the
+substitution $\mathcal{E}(z,\bar z; \Delta^*)\to\mathcal{E}_{\mathrm{max}}(z,\bar z; \Delta^*)$
 Then, the result of each end state of the MC could be tested to see if it
@@
 fact that our spectrum is only approximate. Since the error estimate
-\ref{finalestimate5a}
+\label{finalest4}
 depends
@@
 
+%\cite{Gliozzi:2013ysa}
+\bibitem{Gliozzi:2013ysa}
+  F.~Gliozzi,
+  ``More constraining conformal bootstrap,''
+  Phys.\ Rev.\ Lett.\  {\bf 111} (2013) 161602
+  doi:10.1103/PhysRevLett.111.161602
+  [arXiv:1307.3111 [hep-th]].
+  %%CITATION = doi:10.1103/PhysRevLett.111.161602;%%
+  %101 citations counted in INSPIRE as of 05 Feb 2019
+
+  %\cite{Pappadopulo:2012jk}
+\bibitem{Pappadopulo:2012jk}
+  D.~Pappadopulo, S.~Rychkov, J.~Espin and R.~Rattazzi,
+  ``OPE Convergence in Conformal Field Theory,''
+  Phys.\ Rev.\ D {\bf 86} (2012) 105043
+  doi:10.1103/PhysRevD.86.105043
+  [arXiv:1208.6449 [hep-th]].
+  %%CITATION = doi:10.1103/PhysRevD.86.105043;%%
+  %152 citations counted in INSPIRE as of 05 Feb 2019
+
 \end{thebibliography}

### 2019-02-05 towards_a_grand_unified_script.m

@@ -107,7 +107,7 @@ $MinPrecision=3;
       Export["Res-fixed_Param_Nit="<>ToString[Ndit]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[betad,3]]<>"sigmaMC="<>ToString[N[sigmaMC,3]]<>"dcross="<>ToString[N[dcross,3]]<>"seed="<>ToString[seed]<>"id="<>idTag<>".txt", TotD[[2]]];]
 
 (*MC routine-Chi2*)
-MetroGoFixedSelectiveDirChi2[\[CapitalDelta]\[Phi]_,\[CapitalDelta]LOriginal_,Nz_,Ndit_,prec_,betad_,seed0_,sigmaMC_,dcross_,lmax_,idTag_,sigmaz_]:=Block[{itd, DDldata, sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
+MetroGoFixedSelectiveDirChi2[\[CapitalDelta]\[Phi]_,\[CapitalDelta]LOriginal_,Nz_,Ndit_,prec_,betad_,seed0_,sigmaMC_,dcross_,lmax_,idTag_,sigmaz_,tol_]:=Block[{itd, DDldata, sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
     zsample, Idsample,  PP0, PP1, lr, nr, Errvect, Factor, Factor0, seed=seed0, ppm, DDldataEx, PPEx, QQEx, Idsampleold, ip, nvmax, QQFold,  
     IdsampleEx,zOPE,QQOPE,Calc,coeffTemp,Ident,OPEcoeff,ActionTot,  TotD ,DDldataold,QQold,resultsOld,\[CapitalDelta]LOld,dimToVary,PP,QQsave,\[CapitalDelta]L,dw,errSample,results,nzeros=Length[\[CapitalDelta]LOriginal],fracvio=100,nzerosnew,fracvionew,res,sigmamods=ConstantArray[1,Length[\[CapitalDelta]LOriginal]]}, 
     (*precision*)
[…]

### 2019-02-05 towards_a_grand_unified_script.m
minor changes to restarter

@@ -129,7 +129,8 @@ Idsample = SetPrecision[Table[(zsample[[zv]]*Conjugate[zsample[[zv]]])^\[Capital
     (*Monte Carlo Iteration*)
 TotD =   Reap[ Do[
 $MinPrecision=prec;
-If[fracvio<tol, seed=seed+1;  zsample = Sample[Nz,sigmaz,seed]; 
+If[fracvio<tol, Print["resetting seed"]; 
+seed=seed+1;  zsample = Sample[Nz,sigmaz,seed]; 
 Idsample = SetPrecision[Table[(zsample[[zv]]*Conjugate[zsample[[zv]]])^\[CapitalDelta]\[Phi] -
         ((1 - zsample[[zv]])*(1 - Conjugate[zsample[[zv]]]))^\[CapitalDelta]\[Phi], {zv, 1, Nz}],prec];
     \[CapitalDelta]L = \[CapitalDelta]LOriginal;
@@ -569,19 +570,7 @@ nits=5{500,100,100,100,100,100,100,100,100};
 ParallelTable[mcIterator[1,4,9,\[CapitalDelta]L,\[Beta]list,500,88,1000+50tol,nits,"tol="<>ToString[tol],1/10,tol/10],{tol,1,9}]
 
 
-ParallelTable[metroReturnAvgChi2[100,200,200,10^(-i),deltamc[[2]],10+i,4,"delta2",1/10,10^(-i)],{i,3,4}]
-
-
-ParallelTable[metroReturnAvgChi2[100,1500,200,10^(-i),deltamc[[3]],10+i,4,"delta3",1/10,10^(-i)],{i,3,4}]
-
-
-ParallelTable[metroReturnAvgChi2[100,1500,1000,10^(-i),deltamc[[2]],10+i,4,"delta2",1/10,10^(-i)],{i,3,4}]
-
-
-ParallelTable[metroReturnAvgChi2[100,1500,1000,10^(-i),deltamc[[3]],10+i,4,"delta3",1/10,10^(-i)],{i,3,4}]
-
-
-metroReturnAvgChi2[100,1000,200,10^(-4),deltamc[[3]],10+4,4,"delta3",1/10,10^(-4)]
+ParallelTable[metroReturnAvgChi2[100,1000,200,10^(-4),deltamc[[3]],10+4,4,"delta3",1/10,10^(-4),5 i],{i,1,4}]
 
 
 

### 2019-02-05 towards_a_grand_unified_script.m
minor changes to restarter

@@ -570,7 +570,7 @@ nits=5{500,100,100,100,100,100,100,100,100};
 ParallelTable[mcIterator[1,4,9,\[CapitalDelta]L,\[Beta]list,500,88,1000+50tol,nits,"tol="<>ToString[tol],1/10,tol/10],{tol,1,9}]
 
 
-ParallelTable[metroReturnAvgChi2[100,1000,200,10^(-4),deltamc[[3]],10+4,4,"delta3",1/10,10^(-4),5 i],{i,1,4}]
+ParallelTable[metroReturnAvgChi2[100,1000,200,10^(-4),deltamc[[3]],10+4,4,"delta3",1/10,10^(-4),5i /100 ],{i,1,4}]
 
 
 

### 2019-02-06 towards_a_grand_unified_script.m
towards a convergence check

@@ -109,7 +109,7 @@ $MinPrecision=3;
 (*MC routine-Chi2*)
 MetroGoFixedSelectiveDirChi2[\[CapitalDelta]\[Phi]_,\[CapitalDelta]LOriginal_,Nz_,Ndit_,prec_,betad_,seed0_,sigmaMC_,dcross_,lmax_,idTag_,sigmaz_,tol_]:=Block[{itd, DDldata, sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
     zsample, Idsample,  PP0, PP1, lr, nr, Errvect, Factor, Factor0, seed=seed0, ppm, DDldataEx, PPEx, QQEx, Idsampleold, ip, nvmax, QQFold,  
-    IdsampleEx,zOPE,QQOPE,Calc,coeffTemp,Ident,OPEcoeff,ActionTot,  TotD ,DDldataold,QQold,resultsOld,\[CapitalDelta]LOld,dimToVary,PP,QQsave,\[CapitalDelta]L,dw,errSample,results,nzeros=Length[\[CapitalDelta]LOriginal],fracvio=100,nzerosnew,fracvionew,res,sigmamods=ConstantArray[1,Length[\[CapitalDelta]LOriginal]]}, 
+    IdsampleEx,zOPE,QQOPE,converge=False,Calc,coeffTemp,Ident,OPEcoeff,ActionTot,  TotD ,DDldataold,QQold,resultsOld,\[CapitalDelta]LOld,dimToVary,PP,QQsave,\[CapitalDelta]L,dw,errSample,results,nzeros=Length[\[CapitalDelta]LOriginal],fracvio=100,nzerosnew,fracvionew,res,sigmamods=ConstantArray[1,Length[\[CapitalDelta]LOriginal]]}, 
     (*precision*)
 SetOptions[{RandomReal,RandomVariate},WorkingPrecision->prec];
 $MaxPrecision=prec;
@@ -129,7 +129,9 @@ Idsample = SetPrecision[Table[(zsample[[zv]]*Conjugate[zsample[[zv]]])^\[Capital
     (*Monte Carlo Iteration*)
 TotD =   Reap[ Do[
 $MinPrecision=prec;
-If[fracvio<tol, Print["resetting seed"]; 
+If[fracvio<tol, 
[…]

### 2019-02-06 towards_a_grand_unified_script.m
corrected checker

@@ -260,12 +260,11 @@ Idsample = SetPrecision[Table[(zsample[[zv]]*Conjugate[zsample[[zv]]])^\[Capital
         ((1 - zsample[[zv]])*(1 - Conjugate[zsample[[zv]]]))^\[CapitalDelta]\[Phi], {zv, 1, Nz}],prec];
 
     QQ0 = qQGenDims[\[CapitalDelta]\[Phi],\[CapitalDelta]L,zsample];
-errSample=Table[ \[Rho]intErrorEstimateFt[\[CapitalDelta]\[Phi],\[CapitalDelta]LOriginal[[-1,1]],zsample[[i]],1],{i,1,Nz}];
 
 nzeros=Count[results[[1]],0];
 
-errSample=Table[ \[Rho]intErrorEstimateFt[\[CapitalDelta]\[Phi],\[CapitalDelta]LOriginal[[-1,1]]-2 nzeros,zsample[[i]],1],{i,1,Nz}];
-res=(results[[1]].QQ0-Idsample)errSample;
+errSample=Table[ \[Rho]intErrorEstimateFt[\[CapitalDelta]\[Phi],\[CapitalDelta]LOriginal[[-1,1]](*-2 nzeros*),zsample[[i]],1],{i,1,Nz}];
+res=(results[[1]].QQ0-Idsample)/errSample;
 Export["histogram-res-dist.pdf",Histogram[res,Round[Nz/50]]];
 finalcheck=Abs[res]<1//Thread;
 Return[{results,Count[finalcheck,True]/Nz, nzeros}];
@@ -579,7 +578,7 @@ ParallelTable[metroReturnAvgChi2[100,1000,200,10^(-4),deltamc[[2]],10+10 i,4,"To
 
 
 \[CapitalDelta]L={{3,0},{5,2},{7,4},{9,6},{11,8},{13,10},{15,12},{17,14},{19,16}};
-ParallelTable[metroReturnAvgChi2[100,3000,200,10^(-i),\[CapitalDelta]L,10+i,4,"delta3",1/10,10^(-i)],{i,1,4}]
+ParallelTable[metroReturnAvgChi2[100,3000,200,10^(-i),\[CapitalDelta]L,10+i,4,"bad-delta",1/10,10^(-i),0],{i,1,2}]
 
 
 ccheckMetroWeightedBis[1,\[CapitalDelta]L,100,123,100,1/10]
[…]

### 2019-02-07 towards_a_grand_unified_script.m
recursive apparently working

@@ -197,8 +197,8 @@ Return[{rhovec,(Diagonal[Inverse[Transpose[qq0].w.qq0]])^(-1/2), Sqrt[s/nu]}];
 metroReturnAvg[\[CapitalDelta]\[Phi]_,prec_,nit_,\[Beta]_,\[CapitalDelta]L_,seed_,initialOps_,idtag_]:=Block[{data},
 MetroGoFixedSelectiveDir[\[CapitalDelta]\[Phi],\[CapitalDelta]L,nit,prec,\[Beta],seed,1/10,1/3,Length[\[CapitalDelta]L],ToString[Length[\[CapitalDelta]L]]<>idtag,initialOps];
 data= Get["Res-fixed_Param_Nit="<>ToString[nit]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[\[Beta],3]]<>"sigmaMC="<>ToString[N[1/10,3]]<>"dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]<>"id="<>ToString[Length[\[CapitalDelta]L]]<>idtag<>".txt"];
-Export["Plot-fixed_Param_Nit="<>ToString[nit]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[\[Beta],3]]<>"sigmaMC="<>ToString[N[1/10,3]]<>"dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]<>"id="<>ToString[Length[\[CapitalDelta]L]]<>".pdf",ListPlot[Table[data[[All,2]][[All,i]],{i,1,Length[\[CapitalDelta]L]}],Joined->True,GridLines->Automatic,PlotStyle->Thin,PlotLabel->ToString[Length[\[CapitalDelta]L]]<>"Nit="<>ToString[nit]<>" prec="<>ToString[prec]<>" beta="<>ToString[N[\[Beta],3]]<>" sigmaMC="<>ToString[N[1/10,3]]<>" dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]]];
[…]

### 2019-02-08 towards_a_grand_unified_script.m
optimized sampling

@@ -11,12 +11,13 @@ $MinPrecision=MachinePrecision;
  (*error estimates*)
     \[Rho]intErrorEstimateG[d_, DDs_, z_, \[Gamma]_] := (2^(\[Gamma] + 4*d)*\[Beta]^(\[Gamma] - 4*d)*Gamma[1 - \[Gamma] + 4*d, \[Beta]*DDs])/(Gamma[1 - \[Gamma] + 4*d]*(1 - r^2)^\[Gamma])/.  {r -> Abs[\[Rho]z[z]], \[Beta] -> -Log[Abs[\[Rho]z[z]]]}; 
       \[Rho]intErrorEstimateFt[d_, DDs_, z_, \[Gamma]_] := 
-     v^d*\[Rho]intErrorEstimateG[d, DDs, z, \[Gamma]] + u^d*\[Rho]intErrorEstimateG[d, DDs, 1 - z, \[Gamma]] /. {u -> z*Conjugate[z], v -> (1 - z)*(1 - Conjugate[z])}; 
+    extPrefac[d, 1-z] *\[Rho]intErrorEstimateG[d, DDs, z, \[Gamma]] + extPrefac[d, z] *\[Rho]intErrorEstimateG[d, DDs, 1 - z, \[Gamma]] ; 
      (*coefficients and prefactors*)
  extPrefac[\[CapitalDelta]\[Phi]_, x_] := extPrefac[\[CapitalDelta]\[Phi], x] = ((x)*( Conjugate[x]))^\[CapitalDelta]\[Phi]; 
 	kfunct[\[Beta]_, x_] := kfunct[\[Beta], x] = x^(\[Beta]/2)*Hypergeometric2F1[\[Beta]/2, \[Beta]/2, \[Beta], x]; 
     ConformalBlock[DD_, l_, z_] := ConformalBlock[DD, l, z] =((-1)^l/2^l)*((z*Conjugate[z])/(z - Conjugate[z]))*(kfunct[DD + l, z]*kfunct[DD - l - 2, Conjugate[z]] - 
        kfunct[DD + l, Conjugate[z]]*kfunct[DD - l - 2, z]); 
+
       
       (*random sample of z around (1/2+I0)*)
            Sample[nz_,var_,seed_] := Module[{imax}, SeedRandom[seed];Table[Abs[RandomVariate[NormalDistribution[0, var]]]+
[…]

### 2019-02-08 optim-samp.m
optimized sampling

@@ -1,0 +1,619 @@
+(* ::Package:: *)
+
+(* ::Input:: *)
+(*Define symmetric quantization rho*)
+
+
+CleanSlate;
+$MinPrecision=MachinePrecision;
+  \[Rho]z[z_] := z/(1 + Sqrt[1 - z])^2; 
+ \[Rho]zb[z_] := \[Rho]z[Conjugate[z]]; 
+ (*error estimates*)
+    \[Rho]intErrorEstimateG[d_, DDs_, z_, \[Gamma]_] := (2^(\[Gamma] + 4*d)*\[Beta]^(\[Gamma] - 4*d)*Gamma[1 - \[Gamma] + 4*d, \[Beta]*DDs])/(Gamma[1 - \[Gamma] + 4*d]*(1 - r^2)^\[Gamma])/.  {r -> Abs[\[Rho]z[z]], \[Beta] -> -Log[Abs[\[Rho]z[z]]]}; 
+      \[Rho]intErrorEstimateFt[d_, DDs_, z_, \[Gamma]_] := 
+    extPrefac[d, 1-z] *\[Rho]intErrorEstimateG[d, DDs, z, \[Gamma]] + extPrefac[d, z] *\[Rho]intErrorEstimateG[d, DDs, 1 - z, \[Gamma]] ; 
+     (*coefficients and prefactors*)
+ extPrefac[\[CapitalDelta]\[Phi]_, x_] := extPrefac[\[CapitalDelta]\[Phi], x] = ((x)*( Conjugate[x]))^\[CapitalDelta]\[Phi]; 
+	kfunct[\[Beta]_, x_] := kfunct[\[Beta], x] = x^(\[Beta]/2)*Hypergeometric2F1[\[Beta]/2, \[Beta]/2, \[Beta], x]; 
+    ConformalBlock[DD_, l_, z_] := ConformalBlock[DD, l, z] =((-1)^l/2^l)*((z*Conjugate[z])/(z - Conjugate[z]))*(kfunct[DD + l, z]*kfunct[DD - l - 2, Conjugate[z]] - 
+       kfunct[DD + l, Conjugate[z]]*kfunct[DD - l - 2, z]); 
+
+      
+      (*random sample of z around (1/2+I0)*)
+           Sample[nz_,var_,seed_] := Module[{imax}, SeedRandom[seed];Table[Abs[RandomVariate[NormalDistribution[0, var]]]+
[…]

### 2019-02-08 log_improve.m
Improvements to the logdet routine

@@ -1,0 +1,636 @@
+(* ::Package:: *)
+
+(* ::Input:: *)
+(*Define symmetric quantization rho*)
+
+
+CleanSlate;
+$MinPrecision=MachinePrecision;
+  \[Rho]z[z_] := z/(1 + Sqrt[1 - z])^2; 
+ \[Rho]zb[z_] := \[Rho]z[Conjugate[z]]; 
+ (*error estimates*)
+    \[Rho]intErrorEstimateG[d_, DDs_, z_, \[Gamma]_] := (2^(\[Gamma] + 4*d)*\[Beta]^(\[Gamma] - 4*d)*Gamma[1 - \[Gamma] + 4*d, \[Beta]*DDs])/(Gamma[1 - \[Gamma] + 4*d]*(1 - r^2)^\[Gamma])/.  {r -> Abs[\[Rho]z[z]], \[Beta] -> -Log[Abs[\[Rho]z[z]]]}; 
+      \[Rho]intErrorEstimateFt[d_, DDs_, z_, \[Gamma]_] := 
+     v^d*\[Rho]intErrorEstimateG[d, DDs, z, \[Gamma]] + u^d*\[Rho]intErrorEstimateG[d, DDs, 1 - z, \[Gamma]] /. {u -> z*Conjugate[z], v -> (1 - z)*(1 - Conjugate[z])}; 
+     (*coefficients and prefactors*)
+ extPrefac[\[CapitalDelta]\[Phi]_, x_] := extPrefac[\[CapitalDelta]\[Phi], x] = ((x)*( Conjugate[x]))^\[CapitalDelta]\[Phi]; 
+	kfunct[\[Beta]_, x_] := kfunct[\[Beta], x] = x^(\[Beta]/2)*Hypergeometric2F1[\[Beta]/2, \[Beta]/2, \[Beta], x]; 
+    ConformalBlock[DD_, l_, z_] := ConformalBlock[DD, l, z] =((-1)^l/2^l)*((z*Conjugate[z])/(z - Conjugate[z]))*(kfunct[DD + l, z]*kfunct[DD - l - 2, Conjugate[z]] - 
+       kfunct[DD + l, Conjugate[z]]*kfunct[DD - l - 2, z]); 
+      
+      (*random sample of z around (1/2+I0)*)
+           Sample[nz_,var_,seed_] := Module[{imax}, SeedRandom[seed];Table[Abs[RandomVariate[NormalDistribution[0, var]]]+
[…]

### 2019-02-08 log_improve.m
tests ran on friday

@@ -564,13 +564,13 @@ deltasimport=Import["~/mc-boo/gooddims"]//ToExpression;
 deltamc=Table[Transpose[{deltasimport[[i]],Range[0,16,2]}],{i,1,3}];
 
 
-\[CapitalDelta]L=deltaFree[9];
-a=RandomVariate[NormalDistribution[0,1/10],9];
-\[CapitalDelta]L[[;;,1]]=\[CapitalDelta]L[[;;,1]] (1+ a);
 nits=15{300,100,100,100,100,100,100};
-i=8;
-\[Beta]list=(i/8){1/7,1/9,1/11,1/13,1/14,1/15};
-mcIterator[1,4,9,\[CapitalDelta]L,\[Beta]list,100,88,35+20i,nits,"more-beta-4real"<>ToString[i],1/10,1/10,5]//Timing
+\[Beta]list={1/7,1/9,1/11,1/13,1/14,1/15};
+Table[
+\[CapitalDelta]L=deltaFree[9];
+a=RandomVariate[NormalDistribution[0,10^(-j/6 +1)],9];
+\[CapitalDelta]L[[;;,1]]=\[CapitalDelta]L[[;;,1]] (1+ a);
+mcIterator[1,4,9,\[CapitalDelta]L,\[Beta]list,100,88,35+205j,nits,"convergence-normalsigma"<>ToString[i],1/10,1/10,5]//Timing,{j,3,11}]
 
 
 \[CapitalDelta]L={{3,0},{5,2},{7,4},{9,6},{11,8},{13,10},{15,12},{17,14},{19,16}};

### 2019-02-09 towards_a_grand_unified_script.m
integrated changes

@@ -61,7 +61,8 @@ $MinPrecision=prec;
     SeedRandom[seed];
     Nz=Length[\[CapitalDelta]LOriginal]+1;
   zsample = Sample[Nz,1/100,seed]; 
-Idsample = qQId[\[CapitalDelta]\[Phi],zsample];
+Idsample = extPrefac[\[CapitalDelta]\[Phi], zsample]
+      - extPrefac[\[CapitalDelta]\[Phi], 1-zsample];
     \[CapitalDelta]L = \[CapitalDelta]LOriginal;
   \[CapitalDelta]L[[All,1]] = SetPrecision[\[CapitalDelta]L[[All,1]],prec];
   
@@ -78,7 +79,7 @@ If[\[CapitalDelta]L[[1,1]]<1,\[CapitalDelta]L[[1,1]]=\[CapitalDelta]L[[1,1]]+1];
 (*let every successive run start by varying only the new operator*)
         If[it<Ndit/10&& Nz!=initialOps+1,dimToVary=Nz-1,  dimToVary = RandomInteger[{1,lmax}]];
        (*Shift one dimension by a random amount*)       
-          \[CapitalDelta]L[[dimToVary,1]] = \[CapitalDelta]L[[dimToVary,1]]+ RandomVariate[NormalDistribution[0, sigmaMC]];
+          \[CapitalDelta]L[[dimToVary,1]] = \[CapitalDelta]L[[dimToVary,1]]+ RandomVariate[NormalDistribution[0,sigmaMC]];
 (*Reevaluate coefficients*)
            QQ0[[dimToVary]] = qQGen[\[CapitalDelta]\[Phi],\[CapitalDelta]L[[dimToVary]][[1]],\[CapitalDelta]L[[dimToVary]][[2]],zsample];
           
@@ -193,11 +194,11 @@ r=(qq0.rhovec-id);
 s=r.w.r;
 Return[{rhovec,(Diagonal[Inverse[Transpose[qq0].w.qq0]])^(-1/2), Sqrt[s/nu]}];
 ]
-metroReturnAvg[\[CapitalDelta]\[Phi]_,prec_,nit_,\[Beta]_,\[CapitalDelta]L_,seed_,initialOps_,idtag_]:=Block[{data},
[…]

### 2019-02-09 towards_a_grand_unified_script.m
minor cleanup

@@ -61,8 +61,7 @@ $MinPrecision=prec;
     SeedRandom[seed];
     Nz=Length[\[CapitalDelta]LOriginal]+1;
   zsample = Sample[Nz,1/100,seed]; 
-Idsample = extPrefac[\[CapitalDelta]\[Phi], zsample]
-      - extPrefac[\[CapitalDelta]\[Phi], 1-zsample];
+Idsample = qQId[\[CapitalDelta]\[Phi], zsample];
     \[CapitalDelta]L = \[CapitalDelta]LOriginal;
   \[CapitalDelta]L[[All,1]] = SetPrecision[\[CapitalDelta]L[[All,1]],prec];
   
@@ -75,7 +74,7 @@ $MinPrecision=prec;
           \[CapitalDelta]LOld=\[CapitalDelta]L;
           QQold=QQ0;  
 (*putative Unitarity bound*)
-If[\[CapitalDelta]L[[1,1]]<1,\[CapitalDelta]L[[1,1]]=\[CapitalDelta]L[[1,1]]+1];
+If[\[CapitalDelta]L[[1,1]]<1,\[CapitalDelta]L[[1,1]]=\[CapitalDelta]L[[1,1]]+1/2];
 (*let every successive run start by varying only the new operator*)
         If[it<Ndit/10&& Nz!=initialOps+1,dimToVary=Nz-1,  dimToVary = RandomInteger[{1,lmax}]];
        (*Shift one dimension by a random amount*)       
@@ -209,31 +208,6 @@ Export["zoom-Plot-chi_Param_Nit="<>ToString[nit]<>"prec="<>ToString[prec]<>"beta
 Return[{data[[nit-100;;nit,2]]//Mean,data[[nit-100;;nit,3]]//Mean}];
 ];
 
-checkMetroWeighted[\[CapitalDelta]\[Phi]_,\[CapitalDelta]LOriginal_,prec_,seed_,Nz_,sigmaz_]:=Block[{itd, DDldata, sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
-    zsample, Idsample, PP0, PP1, lr, nr, Errvect, Factor, Factor0, ppm, DDldataEx, PPEx, QQEx, Idsampleold, ip, nvmax, QQFold,  
[…]

### 2019-02-09 towards_a_grand_unified_script.m
some stuff

@@ -545,13 +545,10 @@ a=RandomVariate[NormalDistribution[0,10^(-j/10 )],9]//Abs;
 mcIterator[1,4,9,\[CapitalDelta]L,\[Beta]list,100,88,35+205j,nits,"convergence-normalsigma"<>ToString[j],1/10,1/10,5]//Timing,{j,1,10}]
 
 
+nits=15{300,100,100,100,100,100,100};
+\[Beta]list=(9/10){1/7,1/9,1/11,1/13,1/14,1/15};
 ParallelTable[
-SetOptions[RandomVariate,WorkingPrecision->100];
 \[CapitalDelta]L=deltaFree[9];
-i=2;
-SeedRandom[i j +k];
-a=\[CapitalDelta]L[[;;,1]] RandomVariate[NormalDistribution[0,10^(-i)],9];
-\[CapitalDelta]L[[;;,1]]=\[CapitalDelta]L[[;;,1]] + a;
-metroReturnAvgChi2[100,1000 k,100j,10^(-i),\[CapitalDelta]L,1450+i,4,"nz,nit="<>ToString[j]<>ToString[k],1/10,10^(-i-2),0]//Timing,{k,1,2},{j,1,4}]
-
-
+a=RandomVariate[NormalDistribution[0,10^(-j/10 )],9]//Abs;
+\[CapitalDelta]L[[;;,1]]=\[CapitalDelta]L[[;;,1]] (1+ a);
+mcIterator[1,4,9,\[CapitalDelta]L,\[Beta]list,100,88,35+205j,nits,"smallerbeta-normalsigma"<>ToString[j],1/10,1/10,5]//Timing,{j,1,10}]

### 2019-02-10 towards_a_grand_unified_script.m
rough version of fullMC

@@ -164,7 +164,7 @@ res=(results[[1]].QQ0-Idsample)/errSample;
 nzerosnew=Count[results[[1]],0];
 fracvionew=Count[Abs[res]<1//Thread,False]/Nz;
 
-          If[fracvionew<=fracvio && nzeros>=nzerosnew, fracvio = fracvionew;nzeros=nzerosnew;sigmamods[[dimToVary]] =sigmamods[[dimToVary]] (101/100),
+          If[fracvionew<fracvio && nzeros>=nzerosnew, fracvio = fracvionew;nzeros=nzerosnew;sigmamods[[dimToVary]] =sigmamods[[dimToVary]] (101/100),
           \[CapitalDelta]L=\[CapitalDelta]LOld;QQ0=QQold;   results=resultsOld; sigmamods[[dimToVary]] =sigmamods[[dimToVary]] (99/100)];
 $MinPrecision=10;
    dw=\[CapitalDelta]L[[All,1]];
@@ -203,7 +203,7 @@ Export["zoom-Plot-fixed_Param_Nit="<>ToString[nit]<>"prec="<>ToString[prec]<>"be
 metroReturnAvgChi2[prec_,nit_,Nz_,\[Beta]_,\[CapitalDelta]L_,seed_,initialOps_,idtag_,sigmaz_,sigmaMC_,tol_]:=Block[{data},
 MetroGoFixedSelectiveDirChi2[1,\[CapitalDelta]L,Nz,nit,prec,\[Beta],seed,sigmaMC,1/3,Length[\[CapitalDelta]L],idtag,sigmaz,tol];
 data= Get["Res-chi_Param_Nit="<>ToString[nit]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[\[Beta],3]]<>"sigmaMC="<>ToString[N[sigmaMC,3]]<>"dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]<>"Nz="<>ToString[Nz]<>"id="<>idtag<>".txt"];
[…]

### 2019-02-10 towards_a_grand_unified_script.m
started fullmc test, modified condition on nov min

@@ -129,7 +129,7 @@ Idsample = qQId[\[CapitalDelta]\[Phi],zsample];
     (*Monte Carlo Iteration*)
 TotD =   Reap[ Do[
 $MinPrecision=prec;
-If[fracvio<tol, 
+If[fracvio<=tol, 
 If[converge,Print["Convergence!"];Break[],
 Print["resetting seed"]; 
 seed=seed+1;  zsample = Sample[Nz,sigmaz,seed]; 
@@ -272,7 +272,8 @@ Print["Rejected"];Print[checks[[2;;3]]];seed=seed+finalOps;repCount=repCount+1,P
 ];
 ];
 Export["averages_n_checks"<>"from"<>ToString[initialOps]<>"to"<>ToString[finalOps]<>runid<>"prec="<>ToString[prec]<>"seed="<>ToString[seed]<>"nz="<>ToString[nz]<>".txt", results];
-metroReturnAvgChi2[prec,nits[[1]],Nz_,1,\[CapitalDelta]L,seed,initialOps,idtag_,sigmaz,sigmaMC[[2]],tol]
+If[nzeros<finalOps-initialOps,metroReturnAvgChi2[prec,nits[[1]],Nz_,1,\[CapitalDelta]L,seed,initialOps,idtag_,sigmaz,sigmaMC[[2]],tol],
+Print["Bad logdet. Skipping nov min."]];
 ]
 
 mcPlotDimsAndOPEs[initialOps_,finalOps_,nz_,prec_,seed_,runid_]:=Block[{data,dims,opes,mcDims,mcOpes,refDims,refOpes,nrecs=(finalOps-initialOps) +1},
@@ -563,13 +564,15 @@ a=RandomVariate[NormalDistribution[0,10^(-j/10 )],9]//Abs;
 mcIterator[1,4,9,\[CapitalDelta]L,\[Beta]list,100,88,35+205j,nits,"convergence-normalsigma"<>ToString[j],1/10,1/10,5]//Timing,{j,1,10}]
 
 
+nits=15{300,100,100,100,100,100,100};
+\[Beta]list={1/7,1/9,1/11,1/13,1/14,1/15};
 ParallelTable[
 SetOptions[RandomVariate,WorkingPrecision->100];
 \[CapitalDelta]L=deltaFree[9];
 SeedRandom[i];
[…]

### 2019-02-10 towards_a_grand_unified_script.m
added check to avoid nov when logdet did not converge

@@ -258,7 +258,7 @@ Print["Rejected"];Print[checks[[2;;3]]];seed=seed+finalOps;repCount=repCount+1,P
 Export["averages_n_checks"<>"from"<>ToString[initialOps]<>"to"<>ToString[finalOps]<>runid<>"prec="<>ToString[prec]<>"seed="<>ToString[seed]<>"nz="<>ToString[nz]<>".txt", results];
 ]
 
-fullMC[debugging_,\[CapitalDelta]\[Phi]_,initialOps_,finalOps_,\[CapitalDelta]Linitial_,\[Beta]_,nz_,prec_,seedO_,nits_,runid_,sigmaz_,sigmaMC_,maxReps_,tol_]:=Block[{\[CapitalDelta]L=\[CapitalDelta]Linitial,results,repCount=0,checks,it,seed=seedO,nzeros=finalOps},
+fullMC[debugging_,\[CapitalDelta]\[Phi]_,initialOps_,finalOps_,\[CapitalDelta]Linitial_,\[Beta]_,nz_,prec_,seedO_,nits_,runid_,sigmaz_,sigmaMC_,maxReps_,tol_]:=Block[{\[CapitalDelta]L=\[CapitalDelta]Linitial,results,repCount=0,checks,it,seed=seedO,nzeros=finalOps,logdetConv=True},
 it=initialOps;
 results=Reap[
 While[it<=finalOps,
@@ -268,11 +268,11 @@ If[debugging,Print[checks]];
 If[(checks[[2]]==1) &&(checks[[3]]<=nzeros+1) ,
 nzeros=checks[[3]];it=it+1;repCount=0,
 If[repCount<maxReps,\[CapitalDelta]L[[1;;it,1]]=\[CapitalDelta]L[[1;;it,1]](1+Table[RandomReal[{-1/100,1/100}],{i,1,it}]);
-Print["Rejected"];Print[checks[[2;;3]]];seed=seed+finalOps;repCount=repCount+1,Print["Failed logdet mc"];Break[]]];
+Print["Rejected"];Print[checks[[2;;3]]];seed=seed+finalOps;repCount=repCount+1,Print["Failed logdet mc"]logdetConv=False;Break[]]];
 ];
 ];
[…]

### 2019-02-11 towards_a_grand_unified_script.m
corrected typo:(

@@ -268,7 +268,7 @@ If[debugging,Print[checks]];
 If[(checks[[2]]==1) &&(checks[[3]]<=nzeros+1) ,
 nzeros=checks[[3]];it=it+1;repCount=0,
 If[repCount<maxReps,\[CapitalDelta]L[[1;;it,1]]=\[CapitalDelta]L[[1;;it,1]](1+Table[RandomReal[{-1/100,1/100}],{i,1,it}]);
-Print["Rejected"];Print[checks[[2;;3]]];seed=seed+finalOps;repCount=repCount+1,Print["Failed logdet mc"]logdetConv=False;Break[]]];
+Print["Rejected"];Print[checks[[2;;3]]];seed=seed+finalOps;repCount=repCount+1,Print["Failed logdet mc"];logdetConv=False;Break[]]];
 ];
 ];
 Export["averages_n_checks"<>"from"<>ToString[initialOps]<>"to"<>ToString[finalOps]<>runid<>"prec="<>ToString[prec]<>"seed="<>ToString[seed]<>"nz="<>ToString[nz]<>".txt", results];
@@ -567,12 +567,17 @@ mcIterator[1,4,9,\[CapitalDelta]L,\[Beta]list,100,88,35+205j,nits,"convergence-n
 nits=15{300,100,100,100,100,100,100};
 \[Beta]list={1/7,1/9,1/11,1/13,1/14,1/15};
 ParallelTable[
-SetOptions[RandomVariate,WorkingPrecision->100];
+SetOptions[RandomReal,WorkingPrecision->100];
 \[CapitalDelta]L=deltaFree[9];
-SeedRandom[i];
-a=\[CapitalDelta]L[[;;,1]] RandomVariate[NormalDistribution[0,10^(-i/10)],9]//Abs;
+SeedRandom[i+34];
+a=RandomReal[{-i/10,i/10},9];
 \[CapitalDelta]L[[;;,1]]=\[CapitalDelta]L[[;;,1]] (1+ a);
-{\[CapitalDelta]L,fullMC[True,1,4,9,\[CapitalDelta]L,\[Beta]list,100,100,20i,nits,"First_full_test",1/10,{1/10,1/10000},5,0]}//Timing,{i,1,10}]
[…]

### 2019-02-11 towards_a_grand_unified_script.m
corrected overstringent error

@@ -234,7 +234,7 @@ Idsample = qQId[\[CapitalDelta]\[Phi],zsample];
 
 nzeros=Count[results[[1]],0];
 
-errSample=\[Rho]intErrorEstimateFt[\[CapitalDelta]\[Phi],\[CapitalDelta]LOriginal[[-1,1]],zsample,0] ;
+errSample=\[Rho]intErrorEstimateFt[\[CapitalDelta]\[Phi],\[CapitalDelta]LOriginal[[-nzeros,1]],zsample,0] ;
 res=(results[[1]].QQ0-Idsample)/errSample;
 Export["histogram-res-dist.pdf",Histogram[res,Round[Nz/50]]];
 finalcheck=Abs[res]<1//Thread;
@@ -268,7 +268,8 @@ If[debugging,Print[checks]];
 If[(checks[[2]]==1) &&(checks[[3]]<=nzeros+1) ,
 nzeros=checks[[3]];it=it+1;repCount=0,
 If[repCount<maxReps,\[CapitalDelta]L[[1;;it,1]]=\[CapitalDelta]L[[1;;it,1]](1+Table[RandomReal[{-1/100,1/100}],{i,1,it}]);
-Print["Rejected"];Print[checks[[2;;3]]];seed=seed+finalOps;repCount=repCount+1,Print["Failed logdet mc"];logdetConv=False;Break[]]];
+Print["Rejected"];Print[checks[[2;;3]]];seed=seed+finalOps;repCount=repCount+1,
+Print["Failed logdet mc"];logdetConv=False;Break[]]];
 ];
 ];
 Export["averages_n_checks"<>"from"<>ToString[initialOps]<>"to"<>ToString[finalOps]<>runid<>"prec="<>ToString[prec]<>"seed="<>ToString[seed]<>"nz="<>ToString[nz]<>".txt", results];
@@ -569,10 +570,10 @@ nits=15{300,100,100,100,100,100,100};
 ParallelTable[
 SetOptions[RandomReal,WorkingPrecision->100];
 \[CapitalDelta]L=deltaFree[9];
-SeedRandom[i+34];
-a=RandomReal[{-i/10,i/10},9];
+SeedRandom[i];
+a=RandomReal[{-i/100,i/100},9];
 \[CapitalDelta]L[[;;,1]]=\[CapitalDelta]L[[;;,1]] (1+ a);
[…]

### 2019-02-11 towards_a_grand_unified_script.m
corrected overstringent error

@@ -245,6 +245,8 @@ Return[{results,Count[finalcheck,True]/Nz, nzeros}];
 
 mcIterator[\[CapitalDelta]\[Phi]_,initialOps_,finalOps_,\[CapitalDelta]Linitial_,\[Beta]_,nz_,prec_,seedO_,nits_,runid_,sigmaz_,sigmaMC_,maxReps_]:=Block[{\[CapitalDelta]L=\[CapitalDelta]Linitial,results,repCount=0,checks,it,seed=seedO,nzeros=finalOps},
 it=initialOps;
+
+SetOptions[RandomReal,WorkingPrecision->100];
 results=Reap[
 While[it<=finalOps,
 \[CapitalDelta]L[[1;;it,1]]=Sow[metroReturnAvg[\[CapitalDelta]\[Phi],prec,nits[[it-initialOps+1]],\[Beta][[it-initialOps+1]],\[CapitalDelta]L[[1;;it]],seed+it,initialOps,runid,sigmaMC]][[1]];
@@ -260,6 +262,7 @@ Export["averages_n_checks"<>"from"<>ToString[initialOps]<>"to"<>ToString[finalOp
 
 fullMC[debugging_,\[CapitalDelta]\[Phi]_,initialOps_,finalOps_,\[CapitalDelta]Linitial_,\[Beta]_,nz_,prec_,seedO_,nits_,runid_,sigmaz_,sigmaMC_,maxReps_,tol_]:=Block[{\[CapitalDelta]L=\[CapitalDelta]Linitial,results,repCount=0,checks,it,seed=seedO,nzeros=finalOps,logdetConv=True},
 it=initialOps;
+SetOptions[RandomReal,WorkingPrecision->100];
 results=Reap[
 While[it<=finalOps,
 \[CapitalDelta]L[[1;;it,1]]=Sow[metroReturnAvg[\[CapitalDelta]\[Phi],prec,nits[[it-initialOps+1]],\[Beta][[it-initialOps+1]],\[CapitalDelta]L[[1;;it]],seed+it,initialOps,runid,sigmaMC[[1]]]][[1]];

### 2019-02-11 towards_a_grand_unified_script.m
corrected part specification

@@ -234,7 +234,7 @@ Idsample = qQId[\[CapitalDelta]\[Phi],zsample];
 
 nzeros=Count[results[[1]],0];
 
-errSample=\[Rho]intErrorEstimateFt[\[CapitalDelta]\[Phi],\[CapitalDelta]LOriginal[[-nzeros,1]],zsample,0] ;
+errSample=\[Rho]intErrorEstimateFt[\[CapitalDelta]\[Phi],\[CapitalDelta]LOriginal[[-1-nzeros,1]],zsample,0];
 res=(results[[1]].QQ0-Idsample)/errSample;
 Export["histogram-res-dist.pdf",Histogram[res,Round[Nz/50]]];
 finalcheck=Abs[res]<1//Thread;
@@ -584,4 +584,8 @@ a=RandomReal[{-i/100,i/100},9];
 
 \[CapitalDelta]L=deltaFree[9];
 a=RandomReal[{-1/10,1/10},9];
-\[CapitalDelta]L[[;;,1]]=\[CapitalDelta]L[[;;,1]] (1+ a)
+\[CapitalDelta]L[[;;,1]]=\[CapitalDelta]L[[;;,1]] (1+ a);
+\[CapitalDelta]L[[-0,1]]
+
+
+

### 2019-02-12 draft.tex
corrected average

@@
                      \end{matrix} \right) 
-                     \quad \, \text{and} \, \quad 
+                     \quad \, , \, \quad 
                       \vec{\epsilon} \, \equiv \, 
@@
                                   \vdots
-                                 \end{matrix} \right)  \, .
+                                 \end{matrix} \right)  \, ,
 \end{equation}
@@
 
-The straightforward path is to define a cost function
+The straightforward path would be to define a cost function
 \[
@@
 \subsection{naive approach}
-Given a putative spectrum, the determinant of \ref{matrix-op}
+Given a putative spectrum, the determinant of \ref{matrix-op} for $Nz=N_{Op}$
 should get closer to zero as we approach a physically sensible set of operator
@@
 quickly, and thus it was hard to get the MC routine to solve for a large number
-of operators  ($\sim 7$) at the same time.
+of operators  ($\sim 7$) at the same time, given generic initial conditions.
 
@@
 satisfied Crossing Symmetry with the precision correspoinding to the $\Delta^*$
-considered. Otherwise, it changed the seed of the pseudorandom generator and
-started again the MC.
+considered\footnote{$\vec \rho$ was determined by a modified $\chi^2$
+minimization program. See \ref{cWLS}.}. Otherwise, it changed the seed of the pseudorandom generator and
+started again the MC. The routine ended if at a given number of operators, more
+than a certain number of repetitions was achieved, thus avoiding waste of CPU
+time.
 
@@
 \subsection{cWLS as a way to determine the OPE coefficients}
+\label{cWLS}
 Since the dependence of \ref{cross-check} on $\vec{\rho}$ is linear, for
@@
 one can then take this number and try to minimize it with another Monte Carlo
-routine.
+routine. \emph{I'm still missing consistent results for this part.}
 

### 2019-02-12 towards_a_grand_unified_script.m

@@ -164,6 +164,10 @@ res=(results[[1]].QQ0-Idsample)/errSample;
 nzerosnew=Count[results[[1]],0];
 fracvionew=Count[Abs[res]<1//Thread,False]/Nz;
 
+(*Debugging
+Print[res//Dimensions];
+Print[fracvionew//Dimensions];*)
+
           If[fracvionew<fracvio && nzeros>=nzerosnew, fracvio = fracvionew;nzeros=nzerosnew;sigmamods[[dimToVary]] =sigmamods[[dimToVary]] (101/100),
           \[CapitalDelta]L=\[CapitalDelta]LOld;QQ0=QQold;   results=resultsOld; sigmamods[[dimToVary]] =sigmamods[[dimToVary]] (99/100)];
 $MinPrecision=10;
@@ -198,7 +202,7 @@ MetroGoFixedSelectiveDir[\[CapitalDelta]\[Phi],\[CapitalDelta]L,nit,prec,\[Beta]
 data= Get["Res-fixed_Param_Nit="<>ToString[nit]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[\[Beta],3]]<>"sigmaMC="<>ToString[N[sigmaMC,3]]<>"dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]<>"id="<>ToString[Length[\[CapitalDelta]L]]<>idtag<>".txt"];
 Export["Plot-fixed_Param_Nit="<>ToString[nit]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[\[Beta],3]]<>"sigmaMC="<>ToString[N[sigmaMC,3]]<>"dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]<>"id="<>ToString[Length[\[CapitalDelta]L]]<>".pdf",ListPlot[Table[data[[All,2]][[All,i]],{i,1,Length[\[CapitalDelta]L]}],Joined->True,GridLines->Automatic,PlotStyle->Thin,PlotLegends->\[CapitalDelta]L[[;;,2]],PlotLabel->ToString[Length[\[CapitalDelta]L]]<>"Nit="<>ToString[nit]<>" prec="<>ToString[prec]<>" beta="<>ToString[N[\[Beta],3]]<>" sigmaMC="<>ToString[N[1/10,3]]<>" dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]]];
[…]

### 2019-02-12 draft.tex
probing logdet

@@
 where $\vec \epsilon _{\mathrm{max}}$ is just $\vec \epsilon$ under the
-substitution $\mathcal{E}(z,\bar z; \Delta^*)\to\mathcal{E}_{\mathrm{max}}(z,\bar z; \Delta^*)$
+substitution $\mathcal{E}(z,\bar z;
+\Delta^*)\to\mathcal{E}_{\mathrm{max}}(z,\bar z; \Delta^*)$.
 Then, the result of each end state of the MC could be tested to see if it

### 2019-02-12 towards_a_grand_unified_script.m

@@ -264,6 +264,25 @@ Print["Rejected"];Print[checks[[2;;3]]];seed=seed+finalOps;repCount=repCount+1,P
 Export["averages_n_checks"<>"from"<>ToString[initialOps]<>"to"<>ToString[finalOps]<>runid<>"prec="<>ToString[prec]<>"seed="<>ToString[seed]<>"nz="<>ToString[nz]<>".txt", results];
 ]
 
+(*no check baby*)
+mcIteratorNoCheck[\[CapitalDelta]\[Phi]_,initialOps_,finalOps_,\[CapitalDelta]Linitial_,\[Beta]_,nz_,prec_,seedO_,nits_,runid_,sigmaz_,sigmaMC_,maxReps_]:=Block[{\[CapitalDelta]L=\[CapitalDelta]Linitial,results,repCount=0,checks,it,seed=seedO,nzeros=finalOps},
+it=initialOps;
+SetOptions[RandomReal,WorkingPrecision->100];
+results=Reap[
+While[it<=finalOps,
+\[CapitalDelta]L[[1;;it,1]]=Sow[metroReturnAvg[\[CapitalDelta]\[Phi],prec,nits[[it-initialOps+1]],\[Beta][[it-initialOps+1]],\[CapitalDelta]L[[1;;it]],seed+it,initialOps,runid,sigmaMC]][[1]];
+checks=Sow[ccheckMetroWeightedBis[\[CapitalDelta]\[Phi],\[CapitalDelta]L[[1;;it]],prec,seed+1,nz,sigmaz]];
+If[True,
+nzeros=checks[[3]];it=it+1;repCount=0,
+If[repCount<maxReps,\[CapitalDelta]L[[1;;it,1]]=\[CapitalDelta]L[[1;;it,1]](1+Table[RandomReal[{-1/100,1/100}],{i,1,it}]);
+Print["Rejected"];Print[checks[[2;;3]]];seed=seed+finalOps;repCount=repCount+1,Print["Andato_a"];Break[]]];
+];
+];
+Export["averages_n_checks"<>"from"<>ToString[initialOps]<>"to"<>ToString[finalOps]<>runid<>"prec="<>ToString[prec]<>"seed="<>ToString[seed]<>"nz="<>ToString[nz]<>".txt", results];
+]
+
[…]

### 2019-02-13 towards_a_grand_unified_script.m
improved final plotter

@@ -304,16 +304,18 @@ metroReturnAvgChi2[prec,nits[[1]],nz,1,\[CapitalDelta]L,seed,initialOps,runid,si
 Print["Bad logdet. Skipping nov min."]];
 ]
 
-mcPlotDimsAndOPEs[initialOps_,finalOps_,nz_,prec_,seed_,runid_]:=Block[{data,dims,opes,mcDims,mcOpes,refDims,refOpes,nrecs=(finalOps-initialOps) +1},
+mcPlotDimsAndOPEs[initialOps_,finalOps_,nz_,prec_,seed_,runid_]:=Block[{data,dims,opes,mcDimserr,mcDims,mcOpes,refDims,refOpes,nrecs=(finalOps-initialOps) +1},
 data= Get["averages_n_checks"<>"from"<>ToString[initialOps]<>"to"<>ToString[finalOps]<>runid<>"prec="<>ToString[prec]<>"seed="<>ToString[seed]<>"nz="<>ToString[nz]<>".txt"];
 dims=data[[1,Range[1,2nrecs -1,2]]];
 opes=data[[1,Range[2,2nrecs ,2]]];
 mcDims=ListPlot[dims[[;;,1,1;;4]]//Transpose,PlotLegends->{"l=0","l=2","l=4","l=6"},PlotRange->All];
+mcDimserr=Table[ListPlot[((dims[[;;,1,i]]) - 2i)/2i,PlotRange->{-0.1,0.1}],{i,1,4}];
 refDims=Plot[{2,4,6,8},{x,0,nrecs},PlotStyle->Dashed];
 mcOpes=ListPlot[opes[[;;,1,1,1;;4]]//Transpose,PlotLegends->{"l=0","l=2","l=4","l=6"},PlotRange->All];
 refOpes=Plot[{2,1/3},{x,0,nrecs},PlotStyle->Dashed];
 Export["dims-plot"<>"from"<>ToString[initialOps]<>"to"<>ToString[finalOps]<>runid<>"prec="<>ToString[prec]<>"seed="<>ToString[seed]<>"nz="<>ToString[nz]<>".pdf",Show[mcDims,refDims],PlotLabel->"Dims_from"<>ToString[initialOps]<>"to"<>ToString[finalOps]<>runid<>"prec="<>ToString[prec]<>"seed="<>ToString[seed]];
[…]

### 2019-02-13 towards_a_grand_unified_script.m
added sigma updater

@@ -78,7 +78,7 @@ If[\[CapitalDelta]L[[1,1]]<1,\[CapitalDelta]L[[1,1]]=\[CapitalDelta]L[[1,1]]+1/2
 (*let every successive run start by varying only the new operator*)
         If[it<Ndit/10&& Nz!=initialOps+1,dimToVary=Nz-1,  dimToVary = RandomInteger[{1,lmax}]];
        (*Shift one dimension by a random amount*)       
-          \[CapitalDelta]L[[dimToVary,1]] = \[CapitalDelta]L[[dimToVary,1]]+ RandomVariate[NormalDistribution[0,sigmaMC]];
+          \[CapitalDelta]L[[dimToVary,1]] = \[CapitalDelta]L[[dimToVary,1]]+ RandomVariate[NormalDistribution[0,sigmaMC[[dimToVary]]]];
 (*Reevaluate coefficients*)
            QQ0[[dimToVary]] = qQGen[\[CapitalDelta]\[Phi],\[CapitalDelta]L[[dimToVary]][[1]],\[CapitalDelta]L[[dimToVary]][[2]],zsample];
           
@@ -247,7 +247,7 @@ Return[{results,Count[finalcheck,True]/Nz, nzeros}];
 
 
 
-mcIterator[\[CapitalDelta]\[Phi]_,initialOps_,finalOps_,\[CapitalDelta]Linitial_,\[Beta]_,nz_,prec_,seedO_,nits_,runid_,sigmaz_,sigmaMC_,maxReps_]:=Block[{\[CapitalDelta]L=\[CapitalDelta]Linitial,results,repCount=0,checks,it,seed=seedO,nzeros=finalOps},
+mcIterator[\[CapitalDelta]\[Phi]_,initialOps_,finalOps_,\[CapitalDelta]Linitial_,\[Beta]_,nz_,prec_,seedO_,nits_,runid_,sigmaz_,sigmaMC_,maxReps_]:=Block[{sigmas=sigmaMC,\[CapitalDelta]L=\[CapitalDelta]Linitial,results,repCount=0,checks,it,seed=seedO,nzeros=finalOps},
 it=initialOps;
 
 SetOptions[RandomReal,WorkingPrecision->100];
[…]

### 2019-02-14 towards_a_grand_unified_script.m
varying sigma doesn't seem to improve

@@ -662,4 +662,13 @@ a=ConstantArray[1/10,20];
 mcIteratorNoCheck[1,4,20,\[CapitalDelta]L,\[Beta]list,20,100,376,nits,"testing_update_sigma",1/10,a,1]//Timing
 
 
+\[CapitalDelta]L=deltaFree[20];
+\[CapitalDelta]L[[1;;4,1]]=\[CapitalDelta]L[[1;;4,1]] (1+ 1/2);
+\[CapitalDelta]L[[4;;20,1]]=\[CapitalDelta]L[[4;;20,1]] (1+ 1/10);
+nits=15{300,100,100,100,100,100,100,100,100,100,100,100,100,100,100,100,100};
+a=ConstantArray[1/10,20];
+\[Beta]list={1/5,1/9,1/11,1/13,1/14,1/15,1/20,1/20,1/20,1/25,1/25,1/25,1/25,1/30,1/30,1/30,1/30};
+mcIteratorNoCheck[1,4,20,\[CapitalDelta]L,\[Beta]list,20,100,376,nits,"testing_update_sigma",1/10,a,1]//Timing
+
+
 

### 2019-02-14 towards_a_grand_unified_script.m
varying sigma kinda working

@@ -278,7 +278,8 @@ checks=Sow[ccheckMetroWeightedBis[\[CapitalDelta]\[Phi],\[CapitalDelta]L[[1;;it]
 If[True,
 nzeros=checks[[3]];it=it+1;repCount=0;
 (*Sigma updating*)
-sigmas[[1;;it]]=sigmas[[1;;it]](9/10),
+sigmas[[1;;it-initialOps]]=sigmas[[1;;it-initialOps]](95/100);
+Print[sigmas],
 If[repCount<maxReps,\[CapitalDelta]L[[1;;it,1]]=\[CapitalDelta]L[[1;;it,1]](1+Table[RandomReal[{-1/100,1/100}],{i,1,it}]);
 Print["Rejected"];Print[checks[[2;;3]]];seed=seed+finalOps;repCount=repCount+1,Print["Andato_a"];Break[]]];
 ];
@@ -586,7 +587,7 @@ chi2Functional[(QQ0//Transpose)/errSample,Idsample/errSample,IdentityMatrix[Nz],
 
 
 deltasimport=Import["~/mc-boo/gooddims"]//ToExpression;
-spinAppender[\[CapitalDelta]_]:=Transpose[{\[CapitalDelta],Range[0,16,2]}];
+spinAppender[\[CapitalDelta]_]:=Transpose[{\[CapitalDelta],Range[0,2Length[\[CapitalDelta]]-2,2]}];
 
 
 
@@ -663,12 +664,26 @@ mcIteratorNoCheck[1,4,20,\[CapitalDelta]L,\[Beta]list,20,100,376,nits,"testing_u
 
 
 \[CapitalDelta]L=deltaFree[20];
-\[CapitalDelta]L[[1;;4,1]]=\[CapitalDelta]L[[1;;4,1]] (1+ 1/2);
+\[CapitalDelta]L[[1;;4,1]]=\[CapitalDelta]L[[1;;4,1]] (1+ 3/4);
 \[CapitalDelta]L[[4;;20,1]]=\[CapitalDelta]L[[4;;20,1]] (1+ 1/10);
-nits=15{300,100,100,100,100,100,100,100,100,100,100,100,100,100,100,100,100};
+nits=10{300,100,100,100,100,100,100,100,100,100,100,100,100,100,100,100,100};
 a=ConstantArray[1/10,20];
[…]

### 2019-02-14 towards_a_grand_unified_script.m
coded sigmafac

@@ -268,7 +268,7 @@ Export["averages_n_checks"<>"from"<>ToString[initialOps]<>"to"<>ToString[finalOp
 ]
 
 (*no check baby*)
-mcIteratorNoCheck[\[CapitalDelta]\[Phi]_,initialOps_,finalOps_,\[CapitalDelta]Linitial_,\[Beta]_,nz_,prec_,seedO_,nits_,runid_,sigmaz_,sigmaMC_,maxReps_]:=Block[{\[CapitalDelta]L=\[CapitalDelta]Linitial,sigmas=sigmaMC,results,repCount=0,checks,it,seed=seedO,nzeros=finalOps},
+mcIteratorNoCheck[\[CapitalDelta]\[Phi]_,initialOps_,finalOps_,\[CapitalDelta]Linitial_,\[Beta]_,nz_,prec_,seedO_,nits_,runid_,sigmaz_,sigmaMC_,maxReps_,sigmafac_]:=Block[{\[CapitalDelta]L=\[CapitalDelta]Linitial,sigmas=sigmaMC,results,repCount=0,checks,it,seed=seedO,nzeros=finalOps},
 it=initialOps;
 SetOptions[RandomReal,WorkingPrecision->100];
 results=Reap[
@@ -278,7 +278,7 @@ checks=Sow[ccheckMetroWeightedBis[\[CapitalDelta]\[Phi],\[CapitalDelta]L[[1;;it]
 If[True,
 nzeros=checks[[3]];it=it+1;repCount=0;
 (*Sigma updating*)
-sigmas[[1;;it-initialOps]]=sigmas[[1;;it-initialOps]](95/100);
+sigmas[[1;;it-initialOps]]=sigmas[[1;;it-initialOps]]sigmafac;
 Print[sigmas],
 If[repCount<maxReps,\[CapitalDelta]L[[1;;it,1]]=\[CapitalDelta]L[[1;;it,1]](1+Table[RandomReal[{-1/100,1/100}],{i,1,it}]);
 Print["Rejected"];Print[checks[[2;;3]]];seed=seed+finalOps;repCount=repCount+1,Print["Andato_a"];Break[]]];
@@ -679,11 +679,16 @@ mcIteratorNoCheck[1,4,20,\[CapitalDelta]L,\[Beta]list,20,100,376,nits,"testing_u
[…]

### 2019-02-15 towards_a_grand_unified_script.m
coded sigmafac

@@ -692,3 +692,31 @@ mcIteratorNoCheck[1,4,maxops,\[CapitalDelta]L,\[Beta]list,20,100,1+15i,nits,"sig
 
 
 
+
+
+maxops=8;
+\[CapitalDelta]L=deltaFree[maxops];
+\[CapitalDelta]L[[1;;4,1]]=\[CapitalDelta]L[[1;;4,1]] (1+ 3/4);
+\[CapitalDelta]L[[4;;maxops,1]]=\[CapitalDelta]L[[4;;maxops,1]] (1+ 1/10);
+nits=15{300,100,100,100,100};
+a=ConstantArray[1/10,maxops];
+\[Beta]list={1/5,1/9,1/11,1/13,1/14};
+ParallelTable[
+mcIteratorNoCheck[1,4,maxops,\[CapitalDelta]L,\[Beta]list,20,100,545+10i,nits,"bis-sigmafac="<>ToString[i],1/10,a,1,100/(100+2i)]//Timing,{i,0,9}]
+
+
+
+
+
+Table[mcPlotDimsAndOPEs[4,8,20,100,1+15i,"sigmafac="<>ToString[i]],{i,1,10}]
+
+
+\[CapitalDelta]L=deltaFree[maxops];
+\[CapitalDelta]L[[1;;4,1]]=\[CapitalDelta]L[[1;;4,1]] (1+ 3/4);
+\[CapitalDelta]L[[4;;maxops,1]]=\[CapitalDelta]L[[4;;maxops,1]] (1+ 1/10);
+
+
+\[CapitalDelta]L//N
+
+
+100/120//N

### 2019-02-28 towards_a_grand_unified_script.m
alternating log-chi working

@@ -217,7 +217,7 @@ data= Get["Res-chi_Param_Nit="<>ToString[nit]<>"prec="<>ToString[prec]<>"beta="<
 Export["rel-error-chi2_Nit="<>ToString[nit]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[\[Beta],3]]<>"sigmaMC="<>ToString[N[sigmaMC,3]]<>"dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]<>"id="<>ToString[Length[\[CapitalDelta]L]]<>".pdf",ListPlot[Table[(data[[All,2]][[All,i]]-2i)/(2i),{i,1,Length[\[CapitalDelta]L]}],Joined->True,GridLines->Automatic,PlotStyle->Thin,PlotLegends->\[CapitalDelta]L[[;;,2]],PlotLabel->ToString[Length[\[CapitalDelta]L]]<>"Nit="<>ToString[nit]<>" prec="<>ToString[prec]<>" beta="<>ToString[N[\[Beta],3]]<>" sigmaMC="<>ToString[N[1/10,3]]<>" dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]]];
 Export["zoomed-rel-error-chi2_Nit="<>ToString[nit]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[\[Beta],3]]<>"sigmaMC="<>ToString[N[sigmaMC,3]]<>"dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]<>"id="<>ToString[Length[\[CapitalDelta]L]]<>".pdf",ListPlot[Table[(data[[All,2]][[All,i]]-2i)/(2i),{i,1,Length[\[CapitalDelta]L]}],Joined->True,GridLines->Automatic,PlotStyle->Thin,PlotRange->{-1/10,1/10},PlotLegends->\[CapitalDelta]L[[;;,2]],PlotLabel->ToString[Length[\[CapitalDelta]L]]<>"Nit="<>ToString[nit]<>" prec="<>ToString[prec]<>" beta="<>ToString[N[\[Beta],3]]<>" sigmaMC="<>ToString[N[1/10,3]]<>" dcross="<>ToString[N[1/3,3]]<>"seed="<>ToString[seed]]];
[…]

### 2019-03-02 draft.tex
updated draft. logdet+NoV working up to 12

@@
 \section{Introduction}
-The Conformal Bootstrap offers a way to chart the space of acceptable CFTs.
+The Conformal Bootstrap offers a way to chart the space of unitary and crossing
+symmetric CFTs.
 
@@
 \subsection{naive approach}
-Given a putative spectrum, the determinant of \ref{matrix-op} for $Nz=N_{Op}$
+Given a putative spectrum, the determinant of \ref{matrix-op} (when
+$Nz=N_{Op}+1$)
 should get closer to zero as we approach a physically sensible set of operator
@@
 steps before we allowed the whole spectrum to be optimized. This gave a very
-efficient routine with a large radius of convergence.
+efficient routine with a large radius of convergence. (As of 19/02, we have
+convergence for 50\% above exact dimension for $l=0,2,4,6$ and 10\% for $8\leq l
+\leq 48$, using 3000 iterations for the first step and 1500 for each subsequent
+one).
 
-This recursive step was further improved by using
+For unitary theories, this recursive step was further improved by using
 \ref{error-bound} to bound \ref{matrix-boo} as 
@@
 than a certain number of repetitions was achieved, thus avoiding waste of CPU
-time.
+time. To avoid considering solutions with smaller $\Delta^*$ at each iteration,
+we added the explicit condition of letting the number of zero entries in $\vec
+\rho$ increase at most in one from run to run. This routine managed to get
+relatively good results up to $l=18$, where it became increasingly difficult to
+satisfy the crossing equations.
 
@@
 
+\subsection{Number of Violations (NoV) minimization}
 It is an interesting fact observed in the cases studied so far, that this
@@
 $\vec{\rho}$, which effectively remove higher dimensional operators from the
-OPE, \ref{cross-check} is satisfied.
+OPE, thus reducing $\Delta^*$, \ref{cross-check} is satisfied.
 
@@
 one can then take this number and try to minimize it with another Monte Carlo
-routine. \emph{I'm still missing consistent results for this part.}
+routine. Concretely, this routine takes the naive $\Delta^*$ and given a certain
+number of $z$-points, it counts for how many of these points are the crossing
+equations are violated (NoV). It also counts how many zero coefficients are there in
+the solution. Then, the optimization proceeds by changing one of the dimensions
+whose corresponding OPE coefficients are not zero and then calculating the NoV
+and the number of zero coefficients again. If both the NoV and the number of
+zero OPE coefficients remain constant or decrease, the move is accepted,
+otherwise it is rejected. The optimization terminates when NoV=0 for two
+different sets of z points or when a certain number of iterations is attained.
+
+\section{State of the art}
+The best routine we have so far starts with 4 operators, uses the logdet routine
+to find an approximate set of dimensions and then takes this as a starting
+condition for a NoV minimization, searching to refine the solution and obtain a
+higher number of non-zero OPE coefficients. To this solution a higher operator
+is appended and this new spectrum is taken as the initial condition of another
+logdet MC. This continues as long as the solution satisfies crossing at every
+point (using the effective $\Delta^*$) and each successive step does not add
+more than one extra zero OPE coefficient. I.e.
+$\mathrm{zeros}(\{\Delta_l'\})\leq \mathrm{zeros}(\{\Delta_l\})+1$.
 

### 2019-03-02 towards_a_grand_unified_script.m

@@ -704,9 +704,45 @@ nits=15 (ConstantArray[100,maxops-minops+1]);
 nits[[1]] = 3000;
 \[Beta]list=Table[1/(2i-2),{i,minops,maxops}];
 sigmaChiList=Table[1/1000,{i,minops,maxops}];
-sigmaChiList[[-2]]=10^(-7/2);
+sigmaChiList[[-3]]=10^(-7/2);
+sigmaChiList[[-2]]=10^(-4);
 sigmaChiList[[-1]]=10^(-4);
 mcIteratorFancySchmancy[1,minops,maxops,\[CapitalDelta]L,\[Beta]list,200,100,54,nits,"testing-fancy-autonomous-sigma",1/10,1/10,3,sigmaChiList]
+
+
+minops=4;
+maxops=10;
+\[CapitalDelta]L=deltaFree[maxops];
+\[CapitalDelta]L[[1;;minops,1]]=\[CapitalDelta]L[[1;;minops,1]] (1+ 1/2);
+\[CapitalDelta]L[[minops+1;;maxops,1]]=\[CapitalDelta]L[[minops+1;;maxops,1]] (1+ 1/10);
+nits=15 (ConstantArray[100,maxops-minops+1]);
+nits[[1]] = 3000;
+\[Beta]list=Table[1/(2i-2),{i,minops,maxops}];
+sigmaChiList=Table[1/1000,{i,minops,maxops}];
+sigmaChiList[[-3]]=10^(-7/2);
+sigmaChiList[[-2]]=10^(-4);
+sigmaChiList[[-1]]=10^(-9/2);
+ParallelTable[
+mcIteratorFancySchmancy[1,minops,maxops,\[CapitalDelta]L,\[Beta]list,200,100,10+i,nits,"testing-seed"<>ToString[i],1/10,1/10,0,sigmaChiList]//Timing,{i,1,4}]
+
+
+minops=4;
+maxops=12;
+\[CapitalDelta]L=deltaFree[maxops];
+\[CapitalDelta]L[[1;;minops,1]]=\[CapitalDelta]L[[1;;minops,1]] (1+ 1/2);
+\[CapitalDelta]L[[minops+1;;maxops,1]]=\[CapitalDelta]L[[minops+1;;maxops,1]] (1+ 1/10);
+nits=15 (ConstantArray[100,maxops-minops+1]);
+nits[[1]] = 3000;
[…]

### 2019-03-02 towards_a_grand_unified_script.m
genlog corrected... or not?

@@ -384,7 +384,7 @@ $MinPrecision=prec;
   zsample = Sample[Nz,sigmaz,seed]; 
 Idsample = SetPrecision[Table[(zsample[[zv]]*Conjugate[zsample[[zv]]])^\[CapitalDelta]\[Phi] -
         ((1 - zsample[[zv]])*(1 - Conjugate[zsample[[zv]]]))^\[CapitalDelta]\[Phi], {zv, 1, Nz}],prec];
-    \[CapitalDelta]L = \[CapitalDelta]LOriginal;
+    \[CapitalDelta]L = \[CapitalDelta]LOriginal;Length[\[CapitalDelta]L]
   \[CapitalDelta]L[[All,1]] = SetPrecision[\[CapitalDelta]L[[All,1]],prec];
   
 
@@ -497,7 +497,7 @@ deltaFree[n_]:={2#,2#-2}&/@Range[1,n,1];
 opeFreeRen[n_]:=(renomFactor[2#])^(-1) 2((2#-2)!)^2/(2(2#-2))!&/@Range[1,n,1];
 
 (*PLotters*)
-genLog[\[CapitalDelta]\[Phi]_,\[CapitalDelta]LOriginal_,prec_,seed_,Nz_,sigmaz_]:=Block[{itd, DDldata,  sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
+genLog[\[CapitalDelta]\[Phi]_,\[CapitalDelta]LOriginal_,prec_,seed_,Nz_,sigmaz_,dcross_]:=Block[{itd, DDldata,  sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
     zsample, Idsample, PP0, PP1, lr, nr, Errvect, Factor, Factor0, ppm, DDldataEx, PPEx, QQEx, Idsampleold, ip, nvmax, QQFold,  
     \[CapitalDelta]LOld,dimToVary,PP,QQsave,\[CapitalDelta]L=\[CapitalDelta]LOriginal,dw,smearedaction,\[Rho],rhovec,eqs,rhosol,last,check,results,indices,rhopos,meanrho,sigmarho,finalcheck,errSample,gradientLog,func0}, 
[…]

### 2019-03-02 towards_a_grand_unified_script.m
started tests

@@ -50,9 +50,9 @@ pp=Join[qq0,id];
 Return[Log[Det[pp]^2]]];
 
 (*MC routine*)
-MetroGoFixedSelectiveDir[\[CapitalDelta]\[Phi]_,\[CapitalDelta]LOriginal_,Ndit_,prec_,betad_,seed_,sigmaMC_,dcross_,lmax_,idTag_,initialOps_]:=Block[{itd, DDldata, sigmaz, sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
+MetroGoFixedSelectiveDir[\[CapitalDelta]\[Phi]0_,\[CapitalDelta]LOriginal_,Ndit_,prec_,betad_,seed_,sigmaMC_,dcross_,lmax_,idTag_,initialOps_]:=Block[{itd, DDldata, sigmaz, sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
     zsample, Idsample, Nz, PP0, PP1, lr, nr, Errvect, Factor, Factor0, ppm, DDldataEx, PPEx, QQEx, Idsampleold, ip, nvmax, QQFold,  
-    IdsampleEx,zOPE,QQOPE,Calc,coeffTemp,Ident,OPEcoeff,ActionTot,  TotD ,DDldataold,QQold,\[CapitalDelta]LOld,dimToVary,PP,QQsave,\[CapitalDelta]L,dw,smearedaction}, 
+    IdsampleEx,zOPE,QQOPE,Calc,coeffTemp,Ident,OPEcoeff,ActionTot,  TotD ,DDldataold,QQold,\[CapitalDelta]LOld,dimToVary,PP,QQsave,\[CapitalDelta]L,dw,smearedaction,\[CapitalDelta]\[Phi]=\[CapitalDelta]\[Phi]0}, 
     (*precision*)
 SetOptions[{RandomReal,RandomVariate},WorkingPrecision->prec];
 $MaxPrecision=prec;
@@ -76,15 +76,22 @@ $MinPrecision=prec;
 (*putative Unitarity bound
 If[\[CapitalDelta]L[[1,1]]<1,\[CapitalDelta]L[[1,1]]=\[CapitalDelta]L[[1,1]]+1/2];*)
[…]

### 2019-03-04 towards_a_grand_unified_script.m
testing opstovary

@@ -50,7 +50,7 @@ pp=Join[qq0,id];
 Return[Log[Det[pp]^2]]];
 
 (*MC routine*)
-MetroGoFixedSelectiveDir[\[CapitalDelta]\[Phi]0_,\[CapitalDelta]LOriginal_,Ndit_,prec_,betad_,seed_,sigmaMC_,dcross_,lmax_,idTag_,initialOps_]:=Block[{itd, DDldata, sigmaz, sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
+MetroGoFixedSelectiveDir[\[CapitalDelta]\[Phi]0_,\[CapitalDelta]LOriginal_,Ndit_,prec_,betad_,seed_,sigmaMC_,dcross_,lmax_,idTag_,initialOps_,opsToVary_]:=Block[{itd, DDldata, sigmaz, sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
     zsample, Idsample, Nz, PP0, PP1, lr, nr, Errvect, Factor, Factor0, ppm, DDldataEx, PPEx, QQEx, Idsampleold, ip, nvmax, QQFold,  
     IdsampleEx,zOPE,QQOPE,Calc,coeffTemp,Ident,OPEcoeff,ActionTot,  TotD ,DDldataold,QQold,\[CapitalDelta]LOld,dimToVary,PP,QQsave,\[CapitalDelta]L,dw,smearedaction,\[CapitalDelta]\[Phi]=\[CapitalDelta]\[Phi]0}, 
     (*precision*)
@@ -76,7 +76,7 @@ $MinPrecision=prec;
 (*putative Unitarity bound
 If[\[CapitalDelta]L[[1,1]]<1,\[CapitalDelta]L[[1,1]]=\[CapitalDelta]L[[1,1]]+1/2];*)
 (*let every successive run start by varying only the new operator*)
-        If[it<Ndit/10&& Nz!=initialOps+1,dimToVary=Nz-1,  dimToVary = RandomInteger[{0,lmax}]];
[…]

### 2019-03-04 towards_a_grand_unified_script.m
testing opstovary

@@ -116,9 +116,9 @@ $MinPrecision=3;
       Export["Res-fixed_Param_Nit="<>ToString[Ndit]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[betad,3]]<>"sigmaMC="<>ToString[N[sigmaMC,3]]<>"dcross="<>ToString[N[dcross,3]]<>"seed="<>ToString[seed]<>"id="<>idTag<>".txt", TotD[[2]]];]
 
 (*MC routine-Chi2*)
-MetroGoFixedSelectiveDirChi2[\[CapitalDelta]\[Phi]_,\[CapitalDelta]LOriginal_,Nz_,Ndit_,prec_,betad_,seed0_,sigmaMC_,dcross_,lmax_,idTag_,sigmaz_,tol_]:=Block[{itd, DDldata, sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
+MetroGoFixedSelectiveDirChi2[\[CapitalDelta]\[Phi]0_,\[CapitalDelta]LOriginal_,Nz_,Ndit_,prec_,betad_,seed0_,sigmaMC_,dcross_,lmax_,idTag_,sigmaz_,tol_,opsToVary_]:=Block[{itd, DDldata, sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0, QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
     zsample, Idsample,  PP0, PP1, lr, nr, Errvect, Factor, Factor0, seed=seed0, ppm, DDldataEx, PPEx, QQEx, Idsampleold, ip, nvmax, QQFold,  
-    IdsampleEx,zOPE,QQOPE,converge=False,Calc,coeffTemp,Ident,OPEcoeff,ActionTot,  TotD ,DDldataold,QQold,resultsOld,\[CapitalDelta]LOld,dimToVary,PP,QQsave,\[CapitalDelta]L,dw,errSample,results,nzeros=Length[\[CapitalDelta]LOriginal],fracvio=100,nzerosnew,fracvionew,res,sigmamods=ConstantArray[1,Length[\[CapitalDelta]LOriginal]]}, 
[…]

### 2019-03-22 draft.tex
added multipoint and expanded Gliozzi review

@@
 Linear System. Thus, in order for a solution (that is, a set of OPE coefficients
-satisfying crossing) to exist, each minor should vanish.
+satisfying crossing) to exist, each minor should vanish. More concretely, if one
+is trying to find the dimensions of $N$ operators, one should consider $N$
+different minors, in order to have $N$ trascendental equations and a (hopefully
+non empty)
+set of discrete solutions. Then, the error can be estimated by considering a
+different set of $N$ minors and seeing how much the solutions change. Although
+conceptually clear, this proved to be a major drawback when assesing the
+precision of the results obtained with this method.
+
+Gliozzi's approach gives results for the Lee-Yang edge singularity in $2$, $3$
+and $4$
+dimensions that resemble quite closely the exact ones (for the 2-dimensional
+case) and the numerical results obtained for $D=3,4$.
+
+Drawing inspiration from Gliozzi's work we can posit a functional depending on a
+very big set of $z-$points and all the possible minors thereof. The solutions to
+the crossing equations should then minimize all these determinants.
 
 \section{LogDet implementation}
+We now describe the different stages that our Monte Carlo approach followed.
+As a testing ground, we started with the minimum amount of $z-$points. Then, we
+saw the need of regularizing the numerical singularities that this action had.
+We finally implemented an approach that captures Gliozzi's idea of considering
+several minors.
 \subsection{naive approach}
@@
 
+\subsection{Multiminor approach}
+Searching to avoid the numerical problems posed by taking only $O(10)$ points from a
+distribution, we expanded our $\mathrm{logDet}$ approach to consider a bigger number of
+$z-$points, and adjusting the functional to be
+
+\[
+\begin{aligned}
+  S(\{\Delta_i,l_i\})& = \sum_i \log\Det^2\mathcal{M}_i(\{\Delta_i,l_i\};{z_j}_i)\\
+\end{aligned}
+\]
+
 \section{$\chi^2$ refinement}
@@
 For properly chosen
-points in $z$, not all the inequalties in \ref{cross-check} will be satisfied,
-one can then take this number and try to minimize it with another Monte Carlo
+points in $z$, not all the inequalties in \ref{cross-check} will be satisfied.
+One can then take this number and try to minimize it with another Monte Carlo
 routine. Concretely, this routine takes the naive $\Delta^*$ and given a certain

### 2019-03-22 draft.tex
added multipoint and expanded Gliozzi review

@@
 \begin{aligned}
-  S(\{\Delta_i,l_i\})& = \sum_i \log\Det^2\mathcal{M}_i(\{\Delta_i,l_i\};{z_j}_i)\\
+  S(\{\Delta_i,l_i\})& = \sum_i
+  \log\Det^2\mathcal{M}_i(\{\Delta_i,l_i\};\{z_j\}_i),
 \end{aligned}
 \]
+where 
+$i$ runs over a subset of all the subsets of $\{z_i\}_{i=1}^{N_z}$ containing
+exactly $N_{op}+1$ elements.
+
+For $N_z \sim O(400)$, chosen from a normal distribution centered around $z=1/2$
+and with $\sigma =1/5$, one obtains similar or better results than with the
+cross regularization approach.
 

### 2019-04-21 mc-boo.m
corrected initial move bug

@@ -89,6 +89,24 @@ Print[Dimensions[Idsample]];
 
     QQ0 = qQGenDims[\[CapitalDelta]\[Phi],\[CapitalDelta]L,zsample];
     Print[Dimensions[QQ0]];
+
+(*Initial action Calc*)
+          PP= Join[QQ0,{Idsample}]; 
+          Action = Log[(selectiveMinors[PP//Transpose,#]&/@elems)^2]//Total; 
+         
+QQsave=QQ0;
+(*Brot noch schmieren? *)
+If[dcross!=0,
+smearedaction=Reap[Table[
+           QQ0[[dimToVary]] =qQGen[\[CapitalDelta]\[Phi],\[CapitalDelta]L[[dimToVary]][[1]]+dcross,\[CapitalDelta]L[[dimToVary]][[2]],zsample];  PP = Join[QQ0, {Idsample}]; 
+          Sow[ Log[(selectiveMinors[PP//Transpose,#]&/@elems)^2]//Total ];
+           QQ0[[dimToVary]] =qQGen[\[CapitalDelta]\[Phi],\[CapitalDelta]L[[dimToVary]][[1]]-dcross,\[CapitalDelta]L[[dimToVary]][[2]],zsample];  PP = Join[QQ0, {Idsample}]; 
+          Sow[ Log[(selectiveMinors[PP//Transpose,#]&/@elems)^2]//Total ];
+          QQ0=QQsave,
+          {dimToVary,1,lmax}]];
+
+ Action =Action +Total[smearedaction[[2]]//Flatten] 
+ ];
      
     (*Monte Carlo Iteration*)
 TotD =   Reap[ Do[

### 2019-04-23 draft.tex
added section on minmin

@@
 
+\subsection{Minimum extraction}
+Numerical studies pointed to a great hierarchy between $\partial_{\Delta_0} S$ 
+and $\partial_{\Delta_l} S$ for $l\geq2$, which explained why the oscillations
+for the scalar were much bigger in amplitude than the ones for the higher spin
+operators. This motivated using the configuration corresponding to the absolute
+minimum of the action instead of averaging over the last 100 or so iterations.
+
+This prescription gave results that were consistently better (had errors smaller
+by one order of magnitude). And could be further refined by running an MC
+optimization with 0 temperature. (Pending results.)
+
 \section{$\chi^2$ refinement}

### 2019-05-03 mc-boo-para.m
corrected names and added action plotter

@@ -293,7 +293,7 @@ Return[{data[[-1,2]],data[[-1,3]]}];
 
 
 (*Plotters*)
-logdetPlotnAv[filename_]:=Block[{data,exact,numDims,holdMyBeer,\[CapitalDelta]\[Phi],\[CapitalDelta]L},
+logdetPlotnAv[filename_]:=Block[{data,exact,numDims,dimHolder,\[CapitalDelta]\[Phi],\[CapitalDelta]L},
 data= Get[filename];
 numDims=Length[data[[1,2]]];
 exact=Join[{1},deltaFree[numDims-1][[;;,1]]];
@@ -301,25 +301,27 @@ exact=Join[{1},deltaFree[numDims-1][[;;,1]]];
 Export[filename<>"nat-plot"<>".pdf",ListPlot[Table[data[[All,2]][[All,i]],{i,1,numDims}],Joined->True,GridLines->Automatic,PlotStyle->Thin,PlotLegends->Join[{"ext"},deltaFree[numDims-1][[;;,2]]],PlotLabel->"Full Plot"]];
 Export[filename<>"rel-error"<>".pdf",ListPlot[Table[(data[[All,2]][[All,i]]-exact[[i]])/exact[[i]],{i,1,numDims}],Joined->True,GridLines->Automatic,PlotStyle->Thin,PlotLegends->Join[{"ext"},deltaFree[numDims-1][[;;,2]]],PlotLabel->"Relative Error"]];
 Export[filename<>"zoomed-error"<>".pdf",ListPlot[Table[(data[[All,2]][[All,i]]-exact[[i]])/exact[[i]],{i,1,numDims}],Joined->True,GridLines->Automatic,PlotStyle->Thin,PlotRange->{-1/10,1/10},PlotLegends->Join[{"ext"},deltaFree[numDims-1][[;;,2]]],PlotLabel->"Relative Error (zoom)"]];
-holdMyBeer=Mean[data[[-100;;-1,2]]];
-\[CapitalDelta]L[[All,1]]=holdMyBeer[[2;;-1]];
-\[CapitalDelta]\[Phi]=holdMyBeer[[1]];
[…]

### 2019-05-03 mc-boo-para.m
wrote versatile runner, can now delete wrappers

@@ -273,8 +273,8 @@ Return[{rhovec, Sqrt[s/nu]}]
 ];
 ]
 
-metroReturnAvg[\[CapitalDelta]\[Phi]_,deltaExtMax_,prec_,nit_,\[Beta]_,\[CapitalDelta]L_,seed_,initialOps_,idtag_,sigmaMC_,opsToVary_,sigmaz_,nz_,elems_,dcross_]:=Block[{data,exact=Join[{1},deltaFree[Length[\[CapitalDelta]L]][[;;,1]]]},
-MetroGoFixedSelectiveDir[\[CapitalDelta]\[Phi],deltaExtMax,\[CapitalDelta]L,nit,prec,\[Beta],seed,sigmaMC,dcross,Length[\[CapitalDelta]L],ToString[Length[\[CapitalDelta]L]]<>idtag,initialOps,opsToVary,sigmaz,nz,elems];
+metroReturnAvg[\[CapitalDelta]\[Phi]_,deltaExtMax_,prec_,nit_,\[Beta]_,\[CapitalDelta]L_,seed_,initialOps_,idtag_,sigmaMC_,opsToVary_,sigmaz_,nz_,elems_,dcross_,nProcs_]:=Block[{data,exact=Join[{1},deltaFree[Length[\[CapitalDelta]L]][[;;,1]]]},
+MetroGoFixedSelectiveDir[\[CapitalDelta]\[Phi],deltaExtMax,\[CapitalDelta]L,nit,prec,\[Beta],seed,sigmaMC,dcross,Length[\[CapitalDelta]L],ToString[Length[\[CapitalDelta]L]]<>idtag,initialOps,opsToVary,sigmaz,nz,elems,nProcs];
 data= Get["Res-fixed_Param_Nit="<>ToString[nit]<>"deltaphi0="<>ToString[N[\[CapitalDelta]\[Phi],3]]<>"Nz="<>ToString[nz]<>"sigmaz="<>ToString[N[sigmaz,3]]<>"prec="<>ToString[prec]<>"beta="<>ToString[N[\[Beta],3]]<>"sigmaMC="<>ToString[N[sigmaMC,3]]<>"dcross="<>ToString[N[dcross,3]]<>"seed="<>ToString[seed]<>"id="<>ToString[Length[\[CapitalDelta]L]]<>idtag<>".txt"];
[…]

### 2019-05-04 mc-boo-para.m
sent deprecated routines to the end of file and added clarifying comments

@@ -385,40 +385,18 @@ Return[{results,Count[finalcheck,True]/Nz, nzeros}];
 
 
 
-mcIteratorFullThing[\[CapitalDelta]\[Phi]0_,deltaExtMax_,initialOps_,finalOps_,\[CapitalDelta]Linitial_,\[Beta]_,nz_,prec_,seedO_,nits_,runid_,sigmaz_,sigmaMC_,maxReps_,sigmaChi_,opsToVary_,sigmazLogDet_,nzLogDet_,elems_,dcross_]:=
-Block[{\[CapitalDelta]\[Phi]=\[CapitalDelta]\[Phi]0,\[CapitalDelta]L=\[CapitalDelta]Linitial,results,repCount=0,checks,it,seed=seedO,nzeros=finalOps,dimHolder},
-it=initialOps;
 
-SetOptions[RandomReal,WorkingPrecision->100];
-results=Reap[
-While[it<=finalOps,
-dimHolder=Sow[metroReturnAvg[\[CapitalDelta]\[Phi],deltaExtMax,prec,nits[[it-initialOps+1]],\[Beta][[it-initialOps+1]],\[CapitalDelta]L[[1;;it]],seed+it,initialOps,runid,sigmaMC,opsToVary[[it-initialOps+1]],sigmazLogDet[[it-initialOps+1]],nzLogDet[[it-initialOps+1]],elems[[it-initialOps+1]],dcross]][[1]];
-Print[dimHolder];
-\[CapitalDelta]L[[1;;it,1]]=dimHolder[[2;;-1]];
-\[CapitalDelta]\[Phi]=dimHolder[[1]];
-checks=Sow[ccheckMetroWeightedBis[\[CapitalDelta]\[Phi],\[CapitalDelta]L[[1;;it]],prec,seed+1,nz,sigmaz]];
-Print[checks[[2;;3]]];
-dimHolder=Sow[metroReturnAvgChi2[\[CapitalDelta]\[Phi],deltaExtMax,prec,nits[[it-initialOps+1]],nz,1,\[CapitalDelta]L[[1;;it]],seed+2it,initialOps,runid,sigmaz,sigmaChi[[it-initialOps+1]],0,opsToVary[[it-initialOps+1]]]][[1]];
-Print[dimHolder];
-\[CapitalDelta]L[[1;;it,1]]=dimHolder[[2;;-1]];
-\[CapitalDelta]\[Phi]=dimHolder[[1]];
[…]

### 2019-05-05 mc-boo-para.m
added more comments and corrected action normalization

@@ -68,7 +68,7 @@ spinAppender[\[CapitalDelta]_]:=Transpose[{\[CapitalDelta],Range[0,2Length[\[Cap
 
 (*\[CapitalDelta]\[Phi]0_ Initial external dimension, \[CapitalDelta]LOriginal_Initial spectrum, Ndit_Number of Iterations, prec_precision, betad_1/Temperature, seed_ ,sigmaMC_sigma for the MC step, dcross_regularization radius, 
 lmax_order of the highest operator to vary (redundant at this stage), idTag_string for identifying runs, initialOps_ This tells the routine whether to vary all operators from the begining or just let the newly added one vary on its own for a certain number of steps,
-opsToVary_array with the *)
+opsToVary_array with the index of the operators to be optimized during the montecarlo *)
 
 MetroGoFixedSelectiveDir[\[CapitalDelta]\[Phi]0_,deltaExtMax_,\[CapitalDelta]LOriginal_,Ndit_,prec_,betad_,seed_,sigmaMC_,dcross_,lmax_,idTag_,initialOps_,opsToVary_,sigmaz_,Nz_,elems_,Nprocs_]:=
 Block[{itd, DDldata,  sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0=ConstantArray[0,{Length[\[CapitalDelta]LOriginal],Nprocs,Nz}], QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 
@@ -79,7 +79,7 @@ $MaxPrecision=prec;
 $MinPrecision=prec;
 
     SeedRandom[seed];
-  zsample = Table[Sample[Nz,sigmaz,seed+i],{i,1,Nprocs}]; 
+  zsample = Table[Sample[Nz,sigmaz,seed(i)],{i,1,Nprocs}]; 
   Print[Dimensions[zsample]];
 Idsample = qQId[\[CapitalDelta]\[Phi], zsample];
 Print[Dimensions[Idsample]];
@@ -90,7 +90,7 @@ Action = (ParallelTable[
     QQ0[[;;,idProc,;;]] = qQGenDims[\[CapitalDelta]\[Phi],\[CapitalDelta]L,zsample[[idProc]]];
     Print[Dimensions[QQ0]];
[…]

### 2019-05-05 draft.tex
commented all that could be commented

@@
 
+\subsection{Determination of the external operator's dimension}
+An interesting application of this method is determining the dimension of the
+external operator. The main obstacle to overcome is due to the fact that the
+action depends on this parameter very differently when compared to the exchanged
+operators' dimensions. Also, the contribution of the identity operator, which
+depends only on the external operator, exhibited a spurious runaway
+behaviour that needed to be controlled.
+
+The current working solution is to allow the MC to optimize this parameter but
+to impose artificial bounds on the values it can probe, thus creating bins for
+the external dimension.
+
 \subsection{Recursive with check}
@@
 
+\subsection{Parallel implementation}
+Given the extensive computational cost of evaluating the conformal blocks and
+calculating the minors thereof we devised a parallel algorithm that splits the
+set $\{N_z\}$ into subsets of equal cardinality and assigns the task of
+evaluating the elements of the matrix corresponding to each subset to a
+different kernel. Each kernel then calculates the respective minors and returns
+to the main process their contribution to the action. This entails a
+considerable speedup when working with 20 processors and $O(1000)$ points.
+
 \section{$\chi^2$ refinement}
@@
 $\mathrm{zeros}(\{\Delta_l'\})\leq \mathrm{zeros}(\{\Delta_l\})+1$.
+
+Alternatively, the multipoint approach can determine the dimensions for the 5
+lowest-lying operators with a relative error of $O(10^{-3})$, but it still needs
+to be refined in order to perform properly at higher $l$.
+
+We have also results which agree with Maldacena's theorem %cite Maldacena
+In these simulations we fix the dimension of a higher spin operator ($l=4$ or
+$l=6$) to the value that saturates the unitarity bound, i.e. we forse them to be
+conserved currents. In this case, the multipoint logdet MC shows very clearly
+that all the other operators, including the external operator, find the minimum
+corresponding to the free theory.
 

### 2019-05-05 mc-boo-para.m

@@ -86,6 +86,7 @@ Print[Dimensions[Idsample]];
     \[CapitalDelta]L = \[CapitalDelta]LOriginal;
   \[CapitalDelta]L[[All,1]] = SetPrecision[\[CapitalDelta]L[[All,1]],prec];
   
+  (*Calculate blocks and action for initial conditions*)
 Action = (ParallelTable[
     QQ0[[;;,idProc,;;]] = qQGenDims[\[CapitalDelta]\[Phi],\[CapitalDelta]L,zsample[[idProc]]];
     Print[Dimensions[QQ0]];
@@ -93,7 +94,8 @@ Action = (ParallelTable[
           Log[(selectiveMinors[PP[[;;,idProc,;;]]//Transpose,#]&/@elems)^2]//Total,{idProc,1,Nprocs}] //Total)/(Nprocs*Length[elems]);
          
 QQsave=QQ0;
-(*Brot noch schmieren? *)
+
+(*Smearing. Not compatible with parallel yet. *)
 If[dcross!=0,
 smearedaction=Reap[Table[
            QQ0[[dimToVary]] =qQGen[\[CapitalDelta]\[Phi],\[CapitalDelta]L[[dimToVary]][[1]]+dcross,\[CapitalDelta]L[[dimToVary]][[2]],zsample];  PP = Join[QQ0, {Idsample}]; 
@@ -142,7 +144,6 @@ If[\[CapitalDelta]L[[1,1]]<1,\[CapitalDelta]L[[1,1]]=\[CapitalDelta]L[[1,1]]+1/2
           PP[[;;,idProc,;;]]= Join[QQ0[[;;,idProc,;;]] ,{Idsample[[idProc]]}]; 
           Log[(selectiveMinors[PP[[;;,idProc,;;]]//Transpose,#]&/@elems)^2]//Total,{idProc,1,Nprocs}] //Total)/(Nprocs*Nz);   
      (*End PARALLEL*)
-(*Reevaluate coefficients*)
            
           
  
@@ -154,7 +155,7 @@ If[\[CapitalDelta]L[[1,1]]<1,\[CapitalDelta]L[[1,1]]=\[CapitalDelta]L[[1,1]]+1/2
           \[CapitalDelta]L=\[CapitalDelta]LOld;QQ0=QQold;\[CapitalDelta]\[Phi]=\[CapitalDelta]\[Phi]old; nReject= nReject+1,
           Print["Error"]; Break[]];
 
-	  (*minchecker*)
[…]

### 2019-05-05 mc-boo-para.m
added extra comments

@@ -66,9 +66,14 @@ spinAppender[\[CapitalDelta]_]:=Transpose[{\[CapitalDelta],Range[0,2Length[\[Cap
 
 (*MC routine*)
 
-(*\[CapitalDelta]\[Phi]0_ Initial external dimension, \[CapitalDelta]LOriginal_Initial spectrum, Ndit_Number of Iterations, prec_precision, betad_1/Temperature, seed_ ,sigmaMC_sigma for the MC step, dcross_regularization radius, 
-lmax_order of the highest operator to vary (redundant at this stage), idTag_string for identifying runs, initialOps_ This tells the routine whether to vary all operators from the begining or just let the newly added one vary on its own for a certain number of steps,
-opsToVary_array with the index of the operators to be optimized during the montecarlo *)
+(*\[CapitalDelta]\[Phi]0_ Initial external dimension, 
+deltaExtMax_ max travel for the external dimension,
+	\[CapitalDelta]LOriginal_Initial spectrum, Ndit_Number of Iterations, 
+	prec_precision, betad_1/Temperature, seed_ ,sigmaMC_sigma for the MC step, dcross_regularization radius, 
+lmax_order of the highest operator to vary (redundant at this stage), 
+idTag_string for identifying runs, 
+initialOps_ This tells the routine whether to vary all operators from the begining or just let the newly added one vary on its own for a certain number of steps,
+opsToVary_array with the index of the operators to be optimized during the montecarlo. This follows the order in which they appear in \[CapitalDelta]LOriginal. 0 represents the external operator*)
 
 MetroGoFixedSelectiveDir[\[CapitalDelta]\[Phi]0_,deltaExtMax_,\[CapitalDelta]LOriginal_,Ndit_,prec_,betad_,seed_,sigmaMC_,dcross_,lmax_,idTag_,initialOps_,opsToVary_,sigmaz_,Nz_,elems_,Nprocs_]:=
 Block[{itd, DDldata,  sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0=ConstantArray[0,{Length[\[CapitalDelta]LOriginal],Nprocs,Nz}], QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 

### 2019-05-05 mc-boo-para.m
added extra comments

@@ -73,7 +73,9 @@ deltaExtMax_ max travel for the external dimension,
 lmax_order of the highest operator to vary (redundant at this stage), 
 idTag_string for identifying runs, 
 initialOps_ This tells the routine whether to vary all operators from the begining or just let the newly added one vary on its own for a certain number of steps,
-opsToVary_array with the index of the operators to be optimized during the montecarlo. This follows the order in which they appear in \[CapitalDelta]LOriginal. 0 represents the external operator*)
+opsToVary_array with the index of the operators to be optimized during the montecarlo. This follows the order in which they appear in \[CapitalDelta]LOriginal. 0 represents the external operator
+Nprocs_ number of processors
+*)
 
 MetroGoFixedSelectiveDir[\[CapitalDelta]\[Phi]0_,deltaExtMax_,\[CapitalDelta]LOriginal_,Ndit_,prec_,betad_,seed_,sigmaMC_,dcross_,lmax_,idTag_,initialOps_,opsToVary_,sigmaz_,Nz_,elems_,Nprocs_]:=
 Block[{itd, DDldata,  sigmaD, Action=100000000, Actionnew=0, Action0, DDldatafixed, QQ0=ConstantArray[0,{Length[\[CapitalDelta]LOriginal],Nprocs,Nz}], QQ1, str, Lmax, Nvmax, rr, metcheck, sigmaDini, 

### 2019-05-06 mc-boo-para.m
corrected normalization

@@ -98,7 +98,7 @@ Action = (ParallelTable[
     QQ0[[;;,idProc,;;]] = qQGenDims[\[CapitalDelta]\[Phi],\[CapitalDelta]L,zsample[[idProc]]];
     Print[Dimensions[QQ0]];
           PP[[;;,idProc,;;]]= Join[QQ0[[;;,idProc,;;]] ,{Idsample[[idProc]]}]; 
-          Log[(selectiveMinors[PP[[;;,idProc,;;]]//Transpose,#]&/@elems)^2]//Total,{idProc,1,Nprocs}] //Total)/(Nprocs*Length[elems]);
+          Log[(selectiveMinors[PP[[;;,idProc,;;]]//Transpose,#]&/@elems)^2]//Total,{idProc,1,Nprocs}] //Total)/(Nprocs*Dimensions[elems][[2]]);
          
 QQsave=QQ0;
 
@@ -149,7 +149,7 @@ If[\[CapitalDelta]L[[1,1]]<1,\[CapitalDelta]L[[1,1]]=\[CapitalDelta]L[[1,1]]+1/2
           QQ0[[dimToVary,idProc,;;]] = qQGen[\[CapitalDelta]\[Phi],\[CapitalDelta]L[[dimToVary]][[1]],\[CapitalDelta]L[[dimToVary]][[2]],zsample[[idProc]]];
           ];
           PP[[;;,idProc,;;]]= Join[QQ0[[;;,idProc,;;]] ,{Idsample[[idProc]]}]; 
-          Log[(selectiveMinors[PP[[;;,idProc,;;]]//Transpose,#]&/@elems)^2]//Total,{idProc,1,Nprocs}] //Total)/(Nprocs*Nz);   
+          Log[(selectiveMinors[PP[[;;,idProc,;;]]//Transpose,#]&/@elems)^2]//Total,{idProc,1,Nprocs}] //Total)/(Nprocs*Dimensions[elems][[2]]);   
      (*End PARALLEL*)
            
           
